\chapter{Literature Review}

This is a collection of notes summarizing important papers.  I will give a condensed version of this in the introduction.  

\section{Casimir Books}

Goal: List and reference important equations/chapters.  
I need to figure out the appropriate way to cite chapters/equations/pages within a thesis.  

\subsection{Milonni: Quantum Vacuum}

Milonni~\cite{Milonni1994}

\subsection{Milton: Casimir Effect}
Milton~\cite{Milton2001}

\subsection{Bordag}
Bordag~\cite{Bordag2009}

\subsection{Dalvit: Casimir Effect}
Dalvit~\cite{Dalvit2011}

\subsection{Parsegian: van der Waals forces}

Parsegian~\cite{Parsegian2006}.
Covers van der Waals forces at varying levels of detail.  Finally gets to Green function
point of view for various geometries.  Published prior to major theory breakthroughs.  

\subsection{Israelachivili:Molecular Forces}

Israelachivili~\cite{Israelachvili2011}.
Primarily interested in chemistry effects (and other effects that contribute in addition to 
van der Waals)

\section{Field Theory Books}

\subsection{Brown Quantum Field Theory}

\cite{Brown1994}
Path integrals and stat mech

Field theory.  

Field theory Renormalization

\subsection{Peskin and Schroeder}
\cite{Peskin1995}

\subsection{Srednicki: Quantum Field Theory}
\cite{Srednicki2008}

\subsection{Altland and Simons: Condensed Matter Field Theory}
\cite{Altland2011}

Linear Response

Effective theory

\subsection{Abrikosov:Condensed matter field theory}

\cite{Abrikosov1975}
Thermal field theory

Feynman-Diagram approach to Casimir.
This is tightly related to the version published in papers.  In particular using the 
field theoretic Green function approach.  

\section{Stochastic Books}

\subsection{Oksendahl}

\subsection{Durrett}

\subsection{Gardiner}



\section{Early Papers}

\subsection{Casimir48}


\cite{Casimir1948}

\subsection{CasimirPolder1948}


~\cite{CasimirPolder1948}.  

\subsection{Lifshitz1956}

~\cite{Lifshitz1956}.  

\subsection{Dzyaloshinkii1959}

\cite{Dzyaloshinskii1959}
\subsection{Dzyaloshinksii1961}

\cite{Dzyaloshinskii1961}

\subsection{BarashGinzburg1975}

\cite{Barash1975}
Also comments that resuls derived under limited assumptions also work at finite temperature,
 and with dissipation.  

Introduce Argument principle: $D(\vect{r},\omega)= 1-r_1r_2 e^{-2 r l}$ where $r=\sqrt{k_x^2+k_y^2}$.  
Can write sum over energies as $\sum_n \hbar\omega_n$,
 as the integral against an integral in the complex plane whose poles are at integer spacings.  
In this case, (Eq 6) there are solutions when $D=0$.  So 
\begin{equation}
E=\sum_{\alpha}\frac{\hbar\omega_\alpha}{2}=
-\frac{-1}{2\pi i} \int \frac{dk_xdk_y}{(2\pi)^2}\int_{-i\infty}^{i\infty}d\omega
 \frac{\hbar\omega}{2}\partial_\omega\ln[D(\vect{r},\omega)]
\end{equation}

Also gets used/cited by Schaden's 90s papers.

Comment on studying auxiliary system where frequency is treated as parameter.

Stress the approximation that reduces computing van der Waals forces to computing the Green function.  

Show from microscopic theory (and Maxwell's equations) that the macroscopic 
theory applies in general.
  Average interaction hamiltonian over fluctuations.
  (Similar to Milonni 2010 no?)
  Get relations involving Green tensor   Eq.(25-26)
(They use $g$ to model adiabatic turn-on/turn-off of interaction.)
\begin{equation}
\frac{\omega_n^2}{c^2}\int d\vect{r''} 
\epsilon_{il}(\vect{r},\vect{r''},i|\omega_n|,g)D_{lk}(\vect{r''},\vect{r'},\omega_n,g)
+[\nabla\times\nabla\times D]_{ik}(\vect{r},\vect{r'},\omega_n,g)
 = -\frac{4\pi}{c}\delta_{ik}\delta(\vect{r-r'})
\end{equation}
Change in free energy is 
\begin{equation}
\Delta F = -\frac{k_B T}{2\pi c}\sum_{n}'\omega_n^2\int_0^1\frac{dg}{g}\int d\vect{r'}d\vect{r}
\left[\epsilon_{il}(\vect{r},\vect{r'},i\omega_n,g)
-\delta_{il}\delta(\vect{r-r'})\right]D_{li}(\vect{r'},\vect{r},\omega_n,g)
\end{equation}

Split forces into short-range forces which depend strongly on details,
 and more universal fluctuation physics.
 They allow spatial dispersion on small scales, which is more important for short range forces.  

Eq.35 suggests a connection to QED via the polarization operator, 
\begin{equation}
\Pi_{il}(\vect{r},\vect{r'},\omega_n,\zeta)=\frac{\omega_n^2}{4\pi c}
[\epsilon_{il}(\vect{r},\vect{r'},i|\omega_n|,\zeta)-\delta_{il}\delta(\vect{r-r'})]
\end{equation}
where the full green function for the EM field obeys
\begin{equation}
D = D_0+ \zeta^2D_0\Pi D
\end{equation}
(I think $\zeta$ acts to index contribution of long-wavelength photons,
 $\zeta=0$ is long-wavelength, $\zeta=1$ is all?)
So they quote a familiar looking result: 
\begin{equation}
\Delta F_{\text{long}} =-2k_BT \sum_{n}'\int_0^1 \frac{d\zeta}{\zeta}\zeta^2 \tr[\Pi D]
\end{equation}
Ok, they finally argue that the dielectric constant is dominated by short wavelength physics,
 and finally take $\epsilon_{il}(\vect{r},\vect{r'},i|\omega_n|,\zeta)=\epsilon(\vect{r},i\omega_n)\delta(\vect{r-r'})$.

Then finally show that $D$ is the full Green tensor obeying the usual macroscopic Maxwell equations.  

Just above Eq. 50 they comment that the ``simple'' theory cannot be used with the
 full/exact dielectric function, since it is itself derived as an approximation.  

Last few pages seem to be taking the near-field and far-field limits.  

Generalization to multilayer systems is easy from this point of view,
 since you just tack on more reflection coefficients.  

Comment that anisotropic systems tend to also have torque!

Also cover atom-atom forces from both the dilute limit, and also pointwise interactions.  
They also include magnetic interactions (and seem to have to allow electric-magnetic cross coupling?)

\subsection{Mclachlan1963}

\cite{McLachlan1963}

\section{Experimental Papers:Casimir}

\subsection{Lamoreaux1997}

\cite{Lamoreaux1997}
\subsection{Sushkov2011}

\cite{Sushkov2011}
\subsection{Mohideen1998}
\cite{Mohideen1998} 

\subsection{Chan2001}

\cite{Chan2001}
\subsection{Bressi2002}

\cite{Bressi2002}

\section{Experimental Papers:Casimir-Polder}
\subsection{Harber2005: Cornell BEC}

\cite{Harber2005}
\subsection{Obrecht2007:Cornell BEC}
\cite{Obrecht2007}

\subsection{Antezza chapter}
\cite{Dalvit2011}

\subsection{Alton2011:Atoms-Toroid}

\cite{Alton2011}. 

\subsection{Hung2013:Atom-Microcavity}
 Atoms above 1D Microcavity \cite{Hung2013}


\subsection{Atom-Chips:Folman2000}

\subsection{Atom-Chips:Schneider2003}

\cite{Folman2000,Schneider2003}

\subsection{Cronin-Beams}

\cite{Perreault2005,Lonij2009}

\subsection{Sukenik:Atoms through Cavity}

\cite{Sukenik1993}

(First attempt at Casimir-Polder with CQED).

\subsection{Experimental arguments}

\begin{itemize}
\item Controversies about role of zero temperature pole.  
\item Lamoreaux favors Drude model, Capasso favours plasma model.
\item Seems experiments favour more 
\end{itemize}

\subsection{Geckos: Autumn2002}
Cool, but irrelevant?
\cite{Autumn2002}

\cite{Hawkes2014}

\subsection{Modifications to gravity}

\begin{itemize}
\item Modifications to gravity on $1\mu m$ or $1mm$ scale.  Cite Lamoreaux 2000 Paper.  Gervaci?
Yukawa type forces.  
\item Subtract off Casimir force background.  Tino group.  Use Casimir shield with fairly thick gold to have same Casimir force, and then vary the medium behind it.  Longer range gravity should lead to Requires very careful measurements, on top of carefully extracting Casimir force.   
\end{itemize}

\subsection{Papers: Proximity Force Approximation}

\begin{itemize}
\item Find first use?  Lamoreaux mentions usage.  Derjaguin?\cite{Derjaguin1956} \cite{Blocki1977}
\item Note problem with non-additivity. 
\item Good as order of magnitude estimate?  Useful if very limited curvature, or effectively approximate geometry as planar.  
\end{itemize}

\subsection{Schwinger: Green function methods 1978}

\cite{Schwinger1978, Milton1978}

Scalar green function methods.  Milton book.  
Planes

\subsection{Milton1978}
Spheres

\begin{itemize}
\item Green tensor methods
\item Cite Barton
\item Cite Philbin(?)
\item Cite Vogel and Welsch
\end{itemize}

\section{Papers: Theory- Reflection Matrix}

\begin{enumerate}
\item Cite Balian and Duplantier \cite{Balian1977, Balian1978}.  Multiple scattering of E and B fields
near perfect conductors.  First paper seems to be classical EM.  Second paper applies to Casimir effect.
Studying wrinkling of conductor.  This is an expansion, rather than closed form.  
 \item Cite Lambrecht and French collaborators
   \cite{Lambrecht2006, MaiaNeto2008,Canaguier-Durand2012}.
    Emphasize two-body scattering version between polarizations of EM field.  THen use trace-log=log-det
    trickery for general form.  Plane-plane, sphere-plane etc.  
\item Genet2003 gets Casimir force as scattering problem in quantum optics.  
\item Physical Picture based on generalized Green theorem from 
  SIE~\comment{Stratton}\cite{Stratton1941}.
  \item Boundary Element Methods in Classical Electromagnetism:
    For example see Ch. 8 of \cite{Chew1995}.  
\item Cite Bordag 1985 on quantization with delta functions?  There are others
Kardar and Li too.  %\todo{Put in Borday1985, Kardar and Li citations}
\item Comment on Emig/Buscher showing you can use homogenous green function.
  Relation to Green's theorem.
\item Emig 2004.  Boundary conditions via a version of Green's theorem - can use homogenous Green 
functions given approach current-matching sources.  Introduce delta-functions on \emph{deformed} surfaces.  
\item Emig 2007.  Introduces basic formalism expanded on in Rahi.  
\item Rahi2009.  Integrate out path integral.  Get scattering potential provided by dielectrics between
modes of free geometry.  Lots of basis translations to describe that scattering.  Hubbard-Stratonovich transform
introduces currents coupled via Green functions.  Mostly analytical approach based on solutios in terms of multipoles.
\item Rodriguez2007
Has sum over frequencies as badly oscillating.  Stress-energy tensor.  Finite Difference, Frequency Domain.(FDFD)
Explicit inversion for Green function.  Propose moving to Boundary Element methods as faster.
Also some analysis of worldline methods.
\item Rodriguez2009
\item Reid2009.  Expand Partition function in terms of currents interacting with homogenous Green function.
Carry out integrals using surface-currents.  
Note $N^3$ operations in worst case, and $N\ln N$ for sparse matrices, iterative solvers.  
Crossed Capsules, tetrahedral particles.  \cite{Reid2009}
\item Reid2011.  Follow on from Reid2009.  Introduce magnetic currents and boundary-conditions to get scattering matrices.
(This is the one to work from)\cite{Reid2011}
\item Reid2013.  Explication of Reid2011 as both stress-tensor and path integral quantization.  (and showing
Gauge invariance of results)\cite{Reid2013}
\cite{Emig2004, Emig2007, Rahi2009}
\cite{Kenneth2006}
  Note use of existent analytical methods and similarities to existent 
  numerical FTDT techniques on earlier papers.  
  \cite{Rodriguez2007,Rodriguez2007a, Rodriguez2009}
\item Cite Johnson/Reid for numerical progress.\cite{Reid2009,Reid2011, Reid2013}.
\item Note success, applicability.  \comment{Cite experimental tylenol pill paper}
\end{enumerate}




\subsection{Balian and Duplantier}
\cite{Balian1977} \cite{Balian1978}
\subsection{Lambrecht/MaiaNeto}

\cite{Lambrecht2006}
This paper seems to emphasize the optical network aspect of things.  
Uses the single mirror results to form result for Fabry-Perot cavity.
Treats loss.  
\cite{MaiaNeto2008}
This paper treats plate-sphere results.  (Hmm, I thought they had more to do with this)

\cite{Canaguier-Durand2012}

\subsection{Stratton}
Surface integral equations (Stratton-chu)
\cite{Stratton1941}
Early Emig paper~\cite{Emig2001} computes Casimir energy for corrugated waveguide.
Apparently field splits into two independent scalars.  (TE/TM)
Perfectly conducting boundary conditions, so one scalar obeys Dirichlet, 
the other scalar obeys Neumann BC.
 Interesting for that thought, but otherwise not relevant.  

\subsection{Emig2004}

Paper on deformations showing you can use homogenous green functions within bounding surface.  
\cite{Emig2004}

Quantize EM in general in Lorentz gauge with Fadeev-Popov gauge fixing.  
Introduce restricted partition function that ( I think) enforces EM boundary
conditions on the surfaces. (Note that this idea is exploited in Reids derivation)
\begin{equation}
Z^2(H)=\int D(A^*A)\prod_{\alpha,j}\prod_{\zeta_n}\prod_{\vect{x}\in R_\alpha}
\delta\left[\int_{\vect{x'}\in S_\alpha} \mathcal{L}^\alpha_{j\mu}(\zeta_n;\vect{x},\vect{x'})
  A^\mu(\zeta_n,\vect{x})\right]e^{-S_E[A,A^*]}
\end{equation}
where $R_\alpha$ are auxiliary surfaces, $S_\alpha$ denote surfaces.
$\mathcal{L}^\alpha_{j\mu}$ is differential operator depending on $\epsilon$, normal $\vect{n}_\alpha$.  

Boundary conditions are introduced by appeal to the extinction theorem.  
Tangential components of $B, E$ are continuous across surface.
Normal components of $B, D$ are continuous.

Treat surface constraints at functional delta functions defined on surfaces.
Use Fourier Representation of the delta.  Given quadratic  nature of path integral,
can integrate out fields.

Use Green's theorem to relate full Green function to integrals over surfaces
of of \emph{homogenous} Green functions, where $\epsilon(\omega)$ is constant.  

(Relation to Surface Integral equations?)

\subsection{Emig 2007}
\cite{Emig2007}
\comment{Note: Feinberg and Sucher extended Casimir-Polder to magnetic effects.
Should also include Haakh's work}

Ref 9 is for scalar coupled to dielectric (in terms of scattering matrices).
This is Kenneth/Klich.

Emphasizes a Schwinger like point of view, which attributes field to fluctuating
sources inside bodies.  
Focusing on gauge-invariant quantities.  

Use multipole expansion to derive quantities (Reid and others represent this
with a boundary-element method, which expands fields over surfaces.)

(This paper is the prelude to the 2009 Rahi paper.)

\subsection{Rahi 2009}

Multipole expansion
\cite{Buscher2004}
\cite{Rahi2009}

Extensive bibliography noting connection to Kenneth/Klich, Balian and Duplantier.
Physics connection to Schwinger in terms of fluctuating currents as source.
(Choice amounts to which you emphasize our integrate out first.)

\subsubsection{EM Path Integral}

Start from Lagrangian density
\begin{equation}
\mathcal{L} =\frac{1}{2}(\vect{E\cdot D}-\vect{B\cdot H}).
\end{equation}
Physical fields given in terms of gauge fields
\begin{gather}
\vect{E}=-\nabla\phi-\partial_t\vect{A}\\
\vect{B} = \nabla\times\vect{A}.
\end{gather}
Constitutive relations,
\begin{gather}
\vect{B}(t,\vect{x})=\int_{-\infty}^0 dt' \mur(t-t',\vect{x})\vect{H}(t',\vect{x})
\vect{D}(t,\vect{x})=\int_{-\infty}^0 dt' \epsr(t-t',\vect{x})\vect{E}(t',\vect{x})
\end{gather}
Neglecting spatial dispersion, so get local dielectric.  Also assumed to be 
isotropic.  
Assume action integral is given by up to some time $T$. (They're totally going
to go to imaginary time and temperature with this).
Fourier Expand the fields
\begin{equation}
  \vect{E}(\vect{x},t)=\sum_{n=-\infty}^{\infty} e^{-i\omega_nT}\vect{E}(\omega_n,\vect{x}),
\end{equation}
with $\omega_n=2\pi n/T$.

The electromagnetic action is then
\begin{equation}
S(T) = \frac{T}{2}\sum_{n=-\infty}^\infty \int d\vect{x}
\left(\vect{E_n^*}\frac{1}{\epsr}\vect{E}_n-\vect{B}_n^*\frac{1}{\mur}\vect{B}_n\right)
\end{equation}

Now use Classical equations of motion ($\nabla\times\vect{E}=-\partial_t\vect{B}$)
to eliminate $\vect{B}$ from equations.  This is all still at the classical level.
Action becomes
\begin{align}
S(T) = \frac{T}{2}\sum_{n=-\infty}^\infty \int d\vect{x}
\left[\vect{E_n^*}\epsr\vect{E}_n-\frac{1}{\omega_n^2}
(\nabla\times\vect{E}_n^*)\frac{1}{\mur}(\nabla\times\vect{E}_n)\right]
\end{align}
Now use tensor identity manipulation, where the $k^{th}$ element of $(\nabla\times\vect{A})=$ is
\begin{align}
&\int d^3x (\nabla\times\vect{A}) \cdot f(\nabla\times\vect{B})\\
&=\int d^3x f\epsilon_{ijk}\epsilon_{imn}\partial_jA_k\partial_mB_n\\
%&=-\int d^3x A_k \epsilon_{ijk}\partial_j\epsilon_{imn} f(\partial_mB_n)\\
&=\int d^3x A_k \epsilon_{kji}\partial_j\epsilon_{imn} f(\partial_mB_n)\\
&=\int d^3x \vect{A}\cdot\nabla\times f \nabla\times\vect{B}
\end{align}
Using this integration by parts, the action can be written purely in terms of the electric field
\begin{align}
S(T) = \frac{T}{2}\sum_{n=-\infty}^\infty \int d\vect{x}\vect{E_n^*}
\left[\epsr-\frac{1}{\omega_n^2}\nabla\times\frac{1}{\mur}\nabla\times\right]\vect{E}_n
\end{align}
(Note that this paper uses relative permitivitties.) If you factor out appropriate factors of $\epsilon_0$
you get $c^2$ on magnetic/gradient term.  
This can be further decomposed as
\begin{align}
S(T) = \frac{T}{2}\sum_{n=-\infty}^\infty \int d\vect{x}\vect{E_n^*}
\left[D -\frac{c^2}{\omega_n^2}V\right]\vect{E}_n
\end{align}
where the free space wave operator $D$, and a scattering potential $V$, are given by
\begin{gather}
D=I-\frac{c^2}{\omega_n^2}\nabla\times\nabla\times\\
V=I\frac{\omega_n^2}{c^2}[1-\epsr]-\nabla\times\left(\frac{1}{\mur}-1\right)\nabla\times.
\end{gather}
Note that $D$ has simple expressions for the Green function, since this is just the free-space
EM wave operator.  $V$ can then be treated as a perturbation and its effect solved for.

\subsubsection{Path Integrals}
This is promoted to quantum theory by using the fac that or quadratic Hamiltonians, 
the transition amplitude can be written as 
\begin{equation}
\langle \vect{E}_b|e^{-iHT/\hbar}|\vect{E}_b\rangle = \int D\vect{A} e^{\frac{i}{\hbar}S[T]}
\bigg|_{\vect{E}(t=0)=\vect{E}_a,\vect{E}(t=T)=\vect{E}_b}
\end{equation}
Note that they choose $A_0=0$ gauge-fixing.  ( I think there is an additional implicit
gauge this is fixed by this choice, or that they then use the resulting Classical equations
of motion to produce the result).  

Can get Euclidean path integral by setting $\vect{E}_b=\vect{E}_a$, and tracing over.  Then taking
$T\rightarrow -i\hbar \beta$ yields the path integral expression for the partition function
$Z=\tr[e^{-\beta H}]$ for the EM field.  

Interested in ground state energy at zero temperature.  
\begin{equation}
E=-\frac{1}{\beta}\log Z
\end{equation}
Formally divergent, must be regularized.  If consider energy differences to some reference configuration,
these cutoff dependent contributions drop out.  

Renormalize by considering some reference case.
\begin{equation}
E-E_0=-\frac{1}{\beta}[\log Z-\log Z_0]
\end{equation}

Rotate action from Minkowski to Euclidean, by taking $\epsilon(\omega)\rightarrow\epsilon(i\kappa_n)$
where $\kappa_n=2\pi n/(\hbar\beta c)$.  The traditional Matsubara frequencies are defined as $s_n=c\kappa_n$.
  For other gauges apparently must also rotate $A_0$.  

Exploit the facts that:
1) EM field is real, so $\vect{E}^*(\omega)=\vect{E}(-\omega)$ on the real axis.  
2) Can show response functions also obey $\epsilon(ic\kappa)=\epsilon(-ic\kappa)$.  So only need
to consider integration over $\kappa>0$.  
3) However, this means $\vect{E},\vect{E}^*$ are now treated as independent variables (?)
4) In $\beta\rightarrow \infty$ limit, replace sum with integral:
$\sum_{n\ge 0} \rightarrow \frac{\hbar c\beta}{2\pi}\int d\kappa$
So energy can be written
\begin{equation}
E = -\frac{\hbar c}{2\pi}\int_0^\infty d\kappa \log Z(\kappa).
\end{equation}
where path integral $Z$ is
\begin{align}
Z(\kappa)=\int D\vect{A}D\vect{A}^*\exp\left\{-\beta\int d\vect{x}\vect{E}^*\left[
\left(I+\frac{1}{\kappa^2}\nabla\times\nabla\times\right)+\frac{1}{\kappa^2}V\right]\vect{E}\right\}
\end{align}
where the potential operator is
\begin{equation}
V=I\kappa[1-\epsr(ic\kappa,\vect{x}]-\nabla\times\left(\frac{1}{\mur(ic\kappa,\vect{x})}-1\right)\nabla\times.
\end{equation}

\subsubsection{Green function expansions}
Now an aside on setting up the classical Green functions.
The wave equation associated with the classical action in the absence of media is
\begin{equation}
\left(-I\frac{\omega^2}{c^2}+\nabla\times\nabla\times\right)\vect{E}(\omega,\vect{x})=0
\end{equation}
The Green's function dyadic satisfies the associated equation with delta function source,
\begin{equation}
\left(-I\frac{\omega^2}{c^2}+\nabla\times\nabla\times\right)G^0(\omega,\vect{x},\vect{x'})=I\delta(\vect{x-x'})
\label{eq:A0-Green-x}
\end{equation}
This equation can be solved via a Fourier transform,
\begin{equation}
  G^0(\omega;\vect{k},x')=\int d\vect{x} e^{-i\vect{k\cdot x}} G^0(\omega;\vect{x},\vect{x'})
\end{equation}
Using the Fourier representation of the delta function, the Green function must satisfy
\begin{equation}
\left(-I\frac{\omega^2}{c^2}-\vect{k}\times\vect{k}\times\right)G^0(\omega,\vect{k},\vect{x'})
=Ie^{-i\vect{k}\cdot(\vect{x'})}\label{eq:A0-Green-k}
\end{equation}
This is now a linear matrix equation, which can be solved readily.  We will use 
\begin{equation}
(\vect{k}\times\vect{k}\times)_{ij}=-k^2\left(\delta_{ij}-\frac{k_ik_j}{k^2}\right)=-k^2(P_T)_{ij}
\end{equation}
where we used
\begin{equation}
  \epsilon_{iab}k_a\epsilon_{bcd}k_c = \epsilon_{bia}\epsilon_{bcd}k_ak_c 
= (\delta_{ic}\delta_{ad}-\delta_{id}\delta_{ac})k_ak_c
= k_ik_d-\delta_{id}k^2
\end{equation}
We can use the transverse/longitudinal projectors to write the inverse of the matrix on the LHS. 
\begin{equation}
  I = P_L + P_T \quad P_L^2=P_L\quad P_T^2=P_T\quad P_LP_T=0
\end{equation}
The matrix inverse of the operator in Eq.~(\ref{eq:A0-Green-k}) must satisfy
\begin{equation}
  (aP_L + b P_T)[-\frac{\omega^2}{c^2}(P_L+P_T)-k^2P_T]=I
\end{equation}
for some constants $a$,$b$.  Expanding the above relation out, and equating terms on each side,
we find that 
\begin{align}
  (aP_L + b P_T)[-\frac{\omega^2}{c^2}P_L+(k^2-\omega^2/c^2)P_T]=I
\end{align}
Then $a = -\frac{c^2}{\omega^2}$, and $b=\frac{1}{k^2-\omega^2/c^2}$.  
If we write Eq.~(\ref{eq:A0-Green-k}) as $A G = I e^{-i\vect{k\cdot x'}}$, then the Green function 
can be written as 
\begin{align}
  G^0_{ij}& = A^{-1}_{ik}I_{kj} e^{-i\vect{k\cdot x'}} =e^{-i\vect{k\cdot x'}} \left[-\frac{c^2}{\omega^2}\frac{k_ik_j}{k^2}
    +\frac{1}{k^2-\omega^2/c^2}\left(\delta_{ij}-\frac{k_ik_j}{k^2}\right)\right]
\end{align}
Now simplify the term in front of longitudinal projector (briefly using $\alpha=\omega/c$)
\begin{equation}
  -\frac{1}{\alpha^2}+\frac{1}{k^2-\alpha^2} =  -\frac{k^2-\alpha^2+\alpha^2}{\alpha^2(k^2-\alpha^2)}
=-\frac{k^2}{\alpha^2(k^2-\alpha^2)}
\end{equation}
If we invert the Fourier transform in $k$, then the Green function is written as
\begin{equation}
G^0_{ij}(\omega;\vect{x},\vect{x'})=\int \frac{d\vect{k}}{(2\pi)^3} \frac{e^{i\vect{k}\cdot(\vect{x-x'})}}
{k^2-(\omega/c+i\epsilon)^2}\left(\delta_{ij}-\frac{c^2}{\omega^2}k_ik_j\right),
\end{equation}
where that choice of pole prescription corresponds to choosing outgoing waves, i.e. $e^{ik x}$
The Fourier transform can be evaluated (simple exercise in spherical integrals, and reasoning about 
which way to complete the contour.  
This can also be written as 
\begin{align}
G^0_{ij}(\omega;\vect{x},\vect{x'})&=\left(\delta_{ij}-\frac{c^2}{\omega^2}\partial_i\partial'_j\right)
\int \frac{d\vect{k}}{(2\pi)^3} \frac{e^{i\vect{k}\cdot(\vect{x-x'})}}
{k^2-(\omega/c+i\epsilon)^2}\\
&=\left(\delta_{ij}-\frac{c^2}{\omega^2}\partial_i\partial'_j\right)
\frac{e^{i\omega/c|\vect{x-x'}|}}{4\pi|\vect{x-x'}|}
\end{align}
So far, so standard.  

Can write Green function in terms of states, using $\vect{E}_\alpha(\omega)=
\langle x|\vect{E}_\alpha(\omega)\rangle$, where $\alpha$ is labelling index.
Then the Green function can be expanded in Hilbert space as 
\begin{equation}
  G^0 = \int d\omega' \sum_{\alpha} C_\alpha(\omega')
  \frac{|\vect{E}^\mathrm{reg}_\alpha(\omega')\rangle\langle \vect{E}^\mathrm{reg}_\alpha(\omega')|}
  {\omega'^2/c^2-(\omega/c+i\epsilon)^2}
\end{equation}
where $\vect{E}^\mathrm{reg}$ is a ``regular'' non-singular solution to equations of motion.  
Note these are normalized for EM scattering theory, \emph{not} quantum mechanics,
\begin{equation}
\int d\omega' \sum_{\alpha} C_\alpha(\omega')
  |\vect{E}^\mathrm{reg}_\alpha(\omega')\rangle\langle \vect{E}^\mathrm{reg}_\alpha(\omega')| = I
\end{equation}

Distinguish ``regular'', (solutions to source-free equations), from ``outgoing'' solutions
which must obey outgoing boundary conditions as ``outward'' variable, $\xi_1$ goes to infinity.
Must pick one of the coordinates $\xi_i$ to denote a notion of outward.  
They use the example from spherical scattering of Hankel functions being outgoing, $h_l^{(1)}(kr)\sim \frac{e^{ikr}}{r}$
which is singular at the origin.  This is contrasted with the regular Bessel solution, $j_l^{(1)}$.  
The full outgoing solution is the outgoing solution in $\xi_1$ multiplied by the regular solutions
in $\xi_2,\xi_3$.  

The Green function (carrying out the contour integral in $\omega'$) is:
\begin{equation}
G^0_{ij}=\sum_\alpha C_\alpha(\omega)\left\{\begin{array}{cr}
E_i^\mathrm{out}(\omega,\vect{\xi}) E_j^{\mathrm{reg}*}(\omega,\vect{\xi'}) & \xi_1(\vect{x})>\xi_1'(\vect{x'})\\
E_i^\mathrm{reg}(\omega,\vect{\xi}) E_j^{\mathrm{in}*}(\omega,\vect{\xi'}) & \xi_1(\vect{x})<\xi_1'(\vect{x'})
\end{array}
\right.
\end{equation}
Set $C_\alpha$ using the Wronskian of the regular and outgoing solutions, while the completeness
relation for $\xi_2,\xi_3$ sets the correct ``jump'' condition at $\vect{x=x'}$.  

For imaginary $k$, find incoming and regular solutions increase exponentially with $\xi_1$,
which outgoing solutions descrease exponentially.  

(They  use on-shell to denote only equal frequency components contribute, i.e. $\omega'=\omega$.)

\subsubsection{Translation matrices}

In order to use this formalism, one must be able to translate the matrices to different origins on
different bodies.  

You can use the regular solutions as a basis for expansion - provided you omit the possibly 
singular origin for the outgoing solutions.  
\begin{equation}
\vect{E}^\text{reg}_\alpha(\omega,\vect{x}_i) = \sum_{\beta}\mathcal{V}^{ij}_{\beta,\alpha}(\kappa,\vect{x}_i-\vect{x}_j)
\vect{E}^\text{reg}_\beta(\omega,\vect{x}_j)
\end{equation}
Note that in this formulation, $\vect{x}_i$ is the vector from origin $\mathcal{O}_i$ to a particular 
point, and $\vect{x}_j$ is a vector to the \emph{same} point, but with a different origin.  

So for the outgoing solutions, 
\begin{equation}
\vect{E}^\text{out}_\alpha(\omega,\vect{x}_i) = \sum_{\beta}\mathcal{U}^{ij}_{\beta,\alpha}(\kappa,\vect{x}_i-\vect{x}_j)
\vect{E}^\text{reg}_\beta(\omega,\vect{x}_j),
\end{equation}
provided $x_i$ is not near the origin of its coordinate system.  

(They use $X_{ij}=\vect{x}_i-\vect{x}_j$)

This can be applied to express the Green function when $\vect{x}$ lies on one object,
and $\vect{x'}$ lies on another object.  
\begin{equation}
G^0_{ij}(ic\kappa,\vect{x},\vect{x'})=\sum_{\alpha,\beta} C_\beta(\omega)\left\{\begin{array}{cr}
E_{i,\alpha}^\mathrm{reg}(\kappa,\vect{x}_i) \mathcal{U}^{ij}_{\alpha\beta} E_{j,\beta}^{\mathrm{reg}*}(\omega,\vect{x}_j)
& \text{if $i$ and $j$ are outside each other}\\
E_{i,\alpha}^\mathrm{reg}(\kappa,\vect{x}_i) \mathcal{V}^{ij}_{\alpha\beta} E_{j,\beta}^{\mathrm{in}*}(\omega,\vect{x}_j)
& \text{if $i$ is inside $j$, or $i$ is below $j$ (plane)}\\
E_{i,\alpha}^\mathrm{out}(\kappa,\vect{x}_i) \mathcal{W}^{ji}_{\alpha\beta} E_{j,\beta}^{\mathrm{reg}*}(\omega,\vect{x}_j)
& \text{if $j$ is inside $i$, or $j$ is below $i$ (plane)},
\end{array}\right.\label{eq:G0_expansion}
\end{equation}
where $\mathcal{W}^{ij}_{\alpha\beta}=\frac{C_\alpha}{C_\beta}{\mathcal{V}^{ij}_{\alpha\beta}}^\dag$.

This can be further written in matrix form as 
\begin{equation}
G^0_{ij}(ic\kappa,\vect{x},\vect{x'})=\sum_{\alpha,\beta}C_\beta(\omega)
\left( E_{i,\alpha}^\mathrm{reg}(\kappa,\vect{x}_i), E_{i,\alpha}^\mathrm{out}(\kappa,\vect{x}_i)\right)
\Bigg(
\begin{array}{cc}
\mathcal{U}^{ij}_{\alpha\beta} & \mathcal{V}^{ij}_{\alpha\beta}\\
\mathcal{W}^{ji}_{\alpha\beta} & 0
\end{array}\Bigg)
\Bigg(\begin{array}{c}
 E_{j,\alpha}^{\mathrm{reg}*}(\kappa,\vect{x}_j)\\
E_{j,\alpha}^{\mathrm{in}*}(\kappa,\vect{x}_j)
\end{array}
\Bigg)
\end{equation}
For a given geometry only one of these translation matrices is non-zero, and thus picks out 
one element of the resulting matrix.  

This can be further written in bra-ket notation, where we will define the negative
of the central matrix as $X^{ij}$. (They use BB letters).

(This choice of basis expansion does not work well for intersecting objects - however the 
Johnson choice in terms of triangles works just fine)

\subsubsection{Classical Scattering  theory}

Maxwell's equations can be written in Fourier space as 
\begin{gather}
\nabla\times\vect{E}(\omega,\vect{x}) = i\omega \vect{B}(\omega,\vect{x})\\
\nabla\times\frac{1}{\mur}\vect{B}(\omega,\vect{x}) = -i\frac{\omega}{c^2}\epsr\vect{E}(\omega,\vect{x})
\end{gather}
If we combine the equations, the resulting wave equation can be written as
\begin{equation}
  [H_0+V(\omega,\vect{x})]\vect{E} = \frac{\omega^2}{c^2}\vect{E}(\omega,\vect{x})
\end{equation}
where 
\begin{align}
H_0 = \nabla\times\nabla\times \\
V_0 = I\frac{\omega^2}{c^2}[1-\epsr(\omega,\vect{x})]+\nabla\times\left(\frac{1}{\mur}-1\right)\nabla\times,
\end{align}
and $V_0$ is the same potential operator that showed up in the quantum theory.  

The Lippmann-Schwinger equation says
\begin{equation}
|\vect{E}\rangle = |\vect{E}_0\rangle - G_0V|\vect{E}\rangle,
\end{equation}
where $G_0$ is the free Green operator and $|\vect{E}_0\rangle$ is a solution of the free 
wave equation, i.e. $(H_0-\omega^2/c^2I)|\vect{E}_0\rangle=0$.  (I think This follows from
 defining $|\vect{E}\rangle$ as the original free solution, and some scattered part. Then plug this in
and solve for the implicit equation for $\vect{E}$.)

If you plug this into itself repeatedly, then 
\begin{equation}
|\vect{E}\rangle = |\vect{E}_0\rangle - G_0V(|\vect{E}_0\rangle - G_0V|\vect{E}\rangle)\cdots
=|\vect{E}_0\rangle -G_0T|\vect{E}_0\rangle,
\end{equation}
where the electromagnetic T-operator is
\begin{equation}
  T = V\frac{I}{I+G_0V}= VGG_0^{-1},
\end{equation}
where $G$ is the Green function of the full Hamiltonian: $(-\frac{\omega^2}{c^2}I+H_0+V)G=I$
The free Green function $G_0$ obeys $(-\frac{\omega^2}{c^2}I+H_0)G_0=I$.
  
The $T$ operator is related to the scattering amplitude $\mathcal{F}$.  So if we scatter a wave 
from the exterior of an object, then $|\vect{E}_0\rangle$ is taken to be $|\vect{E}^{\text{reg}}_\alpha\rangle$.
Then using the Green function (\ref{eq:G0_expansion}), the full state can be written as
\begin{equation}
  \vect{E}(\omega,\vect{x}) = \vect{E}^{\text{reg}}_\alpha(\omega,\vect{x}) - \sum_\beta \vect{E}^{\text{out}}_\beta(\omega,\vect{x})
  \int d\vect{x'}d\vect{x''} C_\beta(\omega)\vect{E}^{\text{reg}*}_\beta(\omega,\vect{x'})T(\omega,\vect{x'},\vect{x''})
\vect{E}^{\text{reg}}_\beta(\omega,\vect{x''}).
\end{equation}
This can be further written in Dirac notation (reg-out), 
\begin{equation}
  |\vect{E}(\omega)\rangle = |\vect{E}^{\text{reg}}_\alpha(\omega)\rangle+
  \sum_\beta\mathcal{F}_{\beta\alpha}^{ee}|\vect{E}^{\text{out}}_\beta(\omega)\rangle
\end{equation}
where the external-external scattering amplitude is defined as
\begin{equation}
  \mathcal{F}^{ee}_{\beta,\alpha}=(-1)C_\beta(\omega)\langle \vect{E}^{\text{reg}}_\beta|(\omega)T(\omega)
|\vect{E}^{\text{reg}}_\alpha(\omega)\rangle.
\end{equation}
Similary, for internal-external scattering one has (reg-reg) 
\begin{equation}
  |\vect{E}(\omega)\rangle = |\vect{E}^{\text{reg}}_\alpha(\omega)\rangle+
  \sum_\beta\mathcal{F}_{\beta\alpha}^{ie}|\vect{E}^{\text{reg}}_\beta(\omega)\rangle
\end{equation}
where the internal-external scattering amplitude is defined as
\begin{equation}
  \mathcal{F}^{ie}_{\beta,\alpha}=(-1)C_\beta(\omega)\langle \vect{E}^{\text{in}}_\beta|(\omega)T(\omega)
|\vect{E}^{\text{reg}}_\alpha(\omega)\rangle.
\end{equation}
This corresponds to some outside wave being scattered inwards. 

The converse in internal scattering (hard to actually realize).
In this case $E_0\rightarrow E^{\text{out}}$.  (I'll skip this)

The whole set of scattering amplitudes can be written in matrix form,
\begin{equation}
F = \left(\begin{array}{cc}
    F^{ee} & F^{ei} \\ F^{ie} & F^{ii}
  \end{array}
  \right)
\end{equation}
where the amplitudes are 
\begin{align}
  F^{ee}& = C_\alpha \langle \vect{E}^{\text{reg}}_\alpha|T|\vect{E}^{\text{reg}}_\beta\rangle\\
  F^{ie}& = C_\alpha \langle \vect{E}^{\text{in}}_\alpha|T|\vect{E}^{\text{reg}}_\beta\rangle\\
  F^{ei}& = C_\alpha \langle \vect{E}^{\text{reg}}_\alpha|T|\vect{E}^{\text{out}}_\beta\rangle\\
  F^{ii}& = C_\alpha \langle \vect{E}^{\text{in}}_\alpha|T|\vect{E}^{\text{out}}_\beta\rangle
\end{align}
Seems that you don't actually find $T$, but rather make an ansatz for the solutions appropriate
 to the scattering scenario you are considering, and match the appropriate boundary conditions.
(Well what was the point of all that then?)

\subsubsection{Applying to Partition function}

\subsubsection{Translation Matrices}


\subsection{Kenneth/Klich}
\cite{Kenneth2006}
\cite{Kenneth2008}

\subsection{Reid/Johnson/Rodriguez}

Early numerical papers.
\cite{Rodriguez2007},\cite{Rodriguez2007a}, \cite{Rodriguez2009}.
  Note use of existent analytical methods and similarities to existent numerical 
FTDT techniques Builds on earlier papers (uses better basis) 

Cite Johnson textbook chapter.\cite{Johnson2011}

\subsection{Reid papers}

\cite{Reid2009},\cite{Reid2011}, \cite{Reid2013} 
Note success, applicability.  \comment{Cite experimental tylenol pill paper}

This numerical approach is related to prior multipole scattering approach~\cite{Rahi2009}.
Earlier work chose to expand the scattering amplitudes in terms of mode function
solutions.  In contrast, this work expands the fields at the surfaces using 
boundary elements - in particular triangles.  
This avoids some of the issues of poorly converging summations of solutions that occured in
the multipole method.  Get very similar results, but different choice of basis for calculations.
Multipoles exploit symmetry, while boundary elements are generally applicable, make no assumptions 
about surface.  Other than the bodies are piece-wise continuous.  

Naturally decomposes separate frequencies into independent integral.  Could parallelize that way.
Still have to handle large matrices.  Freely available as ScuffEM package maintained by
 Homer Reid~\cite{ScuffEM2016}.  

\subsection{Reid 2013-Trimmed}

\subsubsection{Intro}

Interaction of effective currents on surfaces.  Get energies/forces/torques from
this matrix, and appropriate derivatives.  Derive things two ways:
i) stress-tensor, ii) path-integral expression.  Get to the same place both ways.  

Point out derivation holds for general temperatures, cite Philbin and Pitaevskii
as pointing out doubts about the canonical case.  

Note use of special function methods that work great when well-suited basis is 
available.  

Reid2013 eliminates the volume integral for a surface integral, where surface currents
enter as fixing EM boundary conditions on some bounding surface.    

The basic formulae are: 
\begin{gather}
  \mathcal{E} = \frac{\hbar}{2\pi}\int_0^\infty d\xi \ln\frac{\det\mathbf{M}(\xi)}{\det\mathbf{M}_\infty(\xi)}
  \\
  \mathcal{F}_i = -\frac{\hbar}{2\pi}\int_0^\infty d\xi \tr\left[\mathbf{M}^{-1}(\xi)
\frac{\partial}{\partial \vect{r}_i}\mathbf{M}(\xi)\right]\\
  \mathcal{T}_i = -\frac{\hbar}{2\pi}\int_0^\infty d\xi \tr\left[\mathbf{M}^{-1}(\xi)
\frac{\partial}{\partial \theta_i}\mathbf{M}(\xi)\right]
\end{gather}
$\xi$ Integrals run over imaginary axis.  Trace runs over all scattering matrix elements.  
Similarity to Rahi work in the matrices.  The meaning however is coupling/scattering between
different bases.  Here it is coupling between surface current elementss.  There it was 
between different field modes.  

Point out their method is more general than mode-function version, 
and better adapted when basis is not good.

Can also use coupling between Homogenous Green functions (re Stratton, and Emig2004 ).

This paper is theoretical - numerical details discussed elsewhere. 

\subsection{Path Integral Derivation}

Do gauge-fixing method of quantization of path integral.
Assuming linear coupling, at zero temperature.  

In contrast with taking ``Weyl gauge'' $A_0=0$, or in terms of Electric fields.    

(Cites a 1985 Bordag Ann. Phys Paper for similarities explicit independence of Fadeev-Popov
gauge fixing).

The action is 
\begin{equation}
  S = \frac{1}{2}\int\frac{d\omega}{2\pi}\int d^3x\,\left[ 
    \epsilon(\omega,\vect{x})|\vect{E}(\omega,\vect{x})|^2 - \mu(\omega,\vect{x})|\vect{H}(\omega,\vect{x})|^2\right]
\end{equation}
Then rewriting $\vect{E},\vect{H}$ in terms of the 4-potentials, the initial Lagrangian density is 
\begin{equation}
 \mathcal{L}= \int\frac{1}{2}\int\frac{d\omega}{2\pi}\,\left[ 
    \epsilon(\omega,\vect{x})(\partial_i A^0+i\omega A^i)(\partial_i {A^0}^*-i\omega A^i)
- \frac{1}{\mu}(\epsilon_{ijk}\partial_jA^k\epsilon_{imn}\partial_mA^n)\right]
\end{equation}
\begin{shaded}
This follows since if we Fourier expand the real-valued time version of this we have 
\begin{equation}
  \int_{0}^T dt e^{i(\omega_n+\omega_mt)}A_nA_m = A_nA_m^*\delta_{n,-m}
\end{equation}
Since the fields are real, $A_n^* = A_{-n}$.  If we take the limit $T\rightarrow\infty$,
the Fourier series is replaced by a sum.  (This will recur again when we confront finite temperature.)
\end{shaded}

Note that this derivation proceeds under the assumption that we will  explicitly enforce 
EM boundary conditions at all surfaces.  Thus we can neglect and ignore any terms involving
$\partial_i\epsilon$.   This stands in contrast to our approach which would attempt to retain 
all such terms.  Our attempts at this path integral for the worldline method would retain these
terms to enforce boundary conditions, and to scale the gradients to be in flat space.  

Now integrate by parts, and Wick rotate to Euclidean space with 
$\{\omega, A^0, {A^0}^*\}\rightarrow \{i\xi,iA_0,iA_0^*\}$.
% \begin{align}
%  \mathcal{L}&= \int\frac{1}{2}\int\frac{d\omega}{2\pi}\,\big[ 
%     \epsilon(\omega,\vect{x})(\partial_i A^0\partial_i {A^0}^*+i\omega A^i\partial_i {A^0}^*
%     -i\omega\partial_iA^0{A^i}^* +\omega^2A^i {A^i}^*)\nonumber\\
%     &- \frac{1}{\mu}(\partial_jA^k\partial_jA^k-\partial_jA^k\partial_kA^j)\big]\\
% % &= \int\frac{1}{2}\int\frac{d\omega}{2\pi}\,\big[ 
% %     \epsilon(\omega,\vect{x})( A^0(-\partial_i\partial^i) {A^0}^*+i\omega A^i\partial_i {A^0}^*
% %     -i\omega\partial_iA^0{A^i}^*+\omega^2A^i {A^i}^*)\nonumber\\
% %     &+ \frac{1}{\mu}(A^k\partial_j\partial_jA^k-A^k\partial_j\partial_kA^j) 
% %     -A^0(\partial_i\epsilon)\partial_iA^{0*} +A^k(\partial_j\frac{1}{\mu})(\partial_jA^k-\partial_kA^j)\big]
% &= \int\frac{1}{2}\int\frac{d\omega}{2\pi}\,\big[ 
%     \epsilon(\omega,\vect{x})( A^{0,*}(-\partial_i\partial^i) A^0-i\omega {A^0}^*(\partial_iA^i+A^i\partial_i\epsilon)
%     -i\omega\partial_iA^0{A^i}^*+\omega^2A^i {A^i}^*)\nonumber\\
%     &+ \frac{1}{\mu}(A^k\partial_j\partial_jA^k-A^k\partial_j\partial_kA^j) 
%     -A^0(\partial_i\epsilon)\partial_iA^{0*} +A^k(\partial_j\frac{1}{\mu})(\partial_jA^k-\partial_kA^j)\big]
% \end{align}

Then split the Lagrangian into: 
\begin{equation}
  \mathcal{L}=\tilde{A}^{\mu,*} \bigg[\left(-\epsilon\xi^2+\frac{1}{\mu}\nabla^2\right)\delta_{\mu\nu} 
  - \alpha_\mu\alpha_\nu\bigg]\tilde{A}^\nu,
\end{equation}
where $(\tilde{A}^0,\tilde{A}^j) = (\sqrt{\epsilon\mu}A^0,\vect{A})$, 
and $\alpha_\mu=(i\sqrt{\epsilon}\xi,\frac{1}{\sqrt{\mu}}\nabla)$.
The pieces in $\alpha_\mu$ are pure gauge degrees of freedom.  Since the boundary conditions will be explicitly
enforced elsewhere, the spatial dependence of $\epsilon$,$\mu$ can be ignored.  

We can equivalently write this as 
\begin{equation}
  \mathcal{L}=\tilde{A}^{\mu,*} [\alpha_\rho\alpha^\rho\delta_{\mu\nu} - \alpha_\mu\alpha_\nu]\tilde{A}^\nu,
\end{equation}
which transparently has the form of a transverse projector.  
This has a null eigenvalue along $\alpha_\mu$, which corresponds to gauge-transformations.  
The null eigenvalue is normally removed within path integrals by using the Fadeev-Popov method for gauge fixing. 
We will discuss gauge-fixing in greater detail later.  
While Fadeev-Popov gauge fixing runs into issues in Non-Abelian theories at very large field strengths,
we are only going to use it for perturbative QED computations, well inside its range of validity.
They then link up with the Fadeev-Popov method by noting that the Fadeev-Popov method handles gauge-fixing by introducing 
\begin{equation}
  1 = \int d\omega \exp\left[-\int_0^{\hbar\beta}d\tau\,\frac{\omega^2}{2} \right]
  \det\bigg[-\frac{\delta G}{\delta f}\bigg]\delta[G(a,f)-\omega]
\end{equation}
There are two factors of unity in this expression.  First, the $\delta$-function and functional
 determinant restrict the integrals to fields with $G(a)=\omega$, while giving each of them equal weight.
Second, there is a Gaussian integral over $\omega$, which is constructed to put the gauge-fixing 
terms in the action in the exponential.

If we use a generalized Lorentz gauge 
\begin{equation}
  G[\tilde{A}^0,\tilde{A}^j] = i\omega \tilde{A}^0 + \partial_j \tilde{A}^j,
\end{equation}
then under the gauge transformation
\begin{equation}
  (\tilde{A}^0,A^j)\rightarrow  (\tilde{A}^0,A^j) + (i\omega,\partial^j)f,
\end{equation}
we can find the functional derivative, 
\begin{equation}
  \frac{\delta G}{\delta f} = \frac{G[A^0+i\omega f,A^j+\partial^jf]  -[A^0,A^j]}{f}
  = (-\omega^2 +\partial_j^2)
\end{equation}
Note that framed in these variables the are no boundary terms at discontinuities.  
This functional determinant is constant, and does not depend on the geometry at all.  

The gauge-fixed Lagrangian is given by
\begin{equation}
  \mathcal{L}=\tilde{A}^{\mu,*} [\alpha_\rho\alpha^\rho\delta_{\mu\nu}
  -(1-\alpha^{-1}_{FP})\alpha_\mu\alpha_\nu]\tilde{A}^\nu
=\tilde{\vect{A}}^{*}[\mathfrak{D}_1-\mathfrak{D}_2]\tilde{\vect{A}},
\end{equation}
where $\alpha_{FP}=1$ corresponds to so-called Feynman gauge, and $\alpha_{FP}=\infty$ is Landau gauge.

The claim is that the partition function is given by 
\begin{equation}
  Z_{EM} = \int [D\tilde{A}]_C e^{-\frac{\beta}{2}\int d\vect{x} \mathcal{L}},
\end{equation}
where $[D\tilde{A}]_C$ integrates over all field conditions that satisfy the boundary conditions.
The boundary conditions will be explicitly enforced via functional delta-functions.  

\subsubsection{EM Boundary Conditions}

Recall that Maxwell's equations in media are:
\begin{align}
  \nabla\cdot\vect{D} =\rho  &\qquad  \nabla\times \vect{E} =-\partial_t \vect{B}\\
 \nabla\cdot\vect{B}=0&\qquad   \nabla\times\vect{H} = -\partial_t \vect{D} +\vect{j} 
\end{align}
In the absence of any free charges or currents, the electromagnetic boundary conditions are given by 
\begin{gather}
  \vect{E}^\|_1 =\vect{E}^\|_2 \qquad  \vect{H}^\|_1 =\vect{H}^\|_2 \\
  B_1^\perp = B_2^\perp\qquad   D_1^\perp = D_2^\perp,
\end{gather}
where the $1,2$ subscripts denote the media the fields are evaluated in.  
These boundary conditions can be enforced by introducing functional $\delta$-functions,
% We can enforce boundary conditions in path integrals via functional delta functions using
% the Fourier representation of the delta function 
% (Cites Bordag, and Kardar and Li)
\begin{equation}
  \delta(\vect{E}^\|_1-\vect{E}^\|_2) = \int D\vect{K} e^{i\int_{\partial \mathcal{O}} d^3\vect{x}\,
    \vect{K}\cdot(\vect{E}^\|_1-\vect{E}^\|_2)},
\end{equation}
where the integral takes place over the interface/boundary of the object~\cite{Bordag1985, Li1992}.
There is a similar expression for the magnetic fields $\vect{H}$, with $\vect{N}$ as the multiplier.  
These Lagrange multiplier fields correspond to the fluctuating surface currents, as they 
are just the currents one must have to enforce the boundary conditions.  

The boundary conditions can be recast in terms of the gauge fields by introducing an appropriate
derivative operators $L^{E,r}$ and $L^{M,r}$.  These operators represent the usual 
relations between the physical fields $\vect{E},\vect{H}$ and the gauge potentials.  

In piece-wise constant media the operators are given by
\begin{equation}
  E_j:=L^{E,r}_{j\mu}\tilde{A}^\mu = -\frac{1}{\sqrt{\epsilon^r\mu^r}}\partial_j \tilde{A}^0+i\xi A^j
  H_j:=L^{M,r}_{j\mu}\tilde{A}^\mu = \frac{1}{\mu^r}\epsilon_{jkl}\partial_k A^l
\end{equation}
In matrix form
\begin{gather}
  L^{E,r} = \left( \begin{array}{cccc} 
      -\frac{1}{\sqrt{\epsilon^r\mu^r}}\partial_x & i\xi & 0 & 0\\
      -\frac{1}{\sqrt{\epsilon^r\mu^r}}\partial_y & 0 &i\xi & 0\\
      -\frac{1}{\sqrt{\epsilon^r\mu^r}}\partial_z & 0 & 0 & i\xi
    \end{array}
  \right)\\
  L^{M,r} = \frac{1}{\mu_r}\left( \begin{array}{cccc} 
      0 & 0 & -\partial_z & \partial_y\\
      0 & \partial_z & 0 & -\partial_x\\
      0 & -\partial_y & \partial_x & 0
    \end{array}
  \right)
  \end{gather}
Note that the piece-wise continuous media assumption lets you commute derivatives and 
material functions with impunity. 

\subsubsection{Integrating out the photon field}

The constrained path integral is meant to only include fields which satisfy the boundary conditions.
This restriction is carried out by inserting the functional delta functions.  The
 resulting path integral over the potential $A^\mu$ is then Gaussian, the integral can be formally carried 
out readily.  This will leave us with a picture of interacting surface currents.  
\begin{align}
  Z_{TE} &= \int D\tilde{A}^\mu \prod_rD\vect{K}_rD\vect{N}_r\exp\bigg\{-\frac{\beta}{2}\int d^3\vect{x}\,
    \tilde{\vect{A}}^{*} [\mathfrak{D}_1 -\mathfrak{D}_2]\tilde{\vect{A}}\nonumber\\
    &\hspace{1cm}  +i\sum_{r} \int_{\partial\mathcal{O}_r}d\vect{x}\,\vect{K}\cdot(
    \vect{L}^{E,r}\tilde{\vect{A}}^{r}-\vect{L}^{E,e}\tilde{\vect{A}}^e)\nonumber\\
    &\hspace{1cm}  +i\sum_{r} \int_{\partial\mathcal{O}_r}d\vect{x}\,\vect{N}\cdot(
    \vect{L}^{M,r}\tilde{\vect{A}}^{r}-\vect{L}^{M,e}\tilde{\vect{A}}^e)\bigg\}
\end{align}
where we use $r$ to denote the body at position $\vect{x}$, and $e$ to denote the exterior.
Note that both the operators, and fields depend on material constants, resulting in a somewhat
overburdened notation.  We have introduced bold-face to denote both vectors and matrices.

We are then free to evaluate the Gaussian integral over $\vect{A}$ in each region, using
\begin{equation}
  \int D\phi e^{-\frac{\beta}{2}\int d^3\vect{x}\, [\phi^i \mathcal{L}_{ij}\phi^j +i+\psi^k\phi_k]}
= e^{-\frac{1}{2\beta}\int d^3\vect{x}\,\psi^k G_{km} \psi^m},
\end{equation}
where $\mathcal{L}_{ij}G^{jm} = \delta_{i}^m$, and $G$ is the Green function corresponding to $L$.
The partition function can be slightly re-arranged to a more suitable form,
\begin{align}
  Z_{TE} &= \int D\tilde{A}^\mu \prod_rD\vect{K}_rD\vect{N}_re^{-S_{A,e}-\sum_rS_{A,r}+i\sum_rC_r-iC_e}
\end{align}
where 
\begin{align}
  S_{A,e}&=\frac{\beta}{2}\int_e d^3\vect{x}\,  \tilde{\vect{A}}^{e,*} \mathfrak{D}^e\tilde{\vect{A}}^e \\
 S_{A,r}&=\frac{\beta}{2}\int_r d^3\vect{x}\, \tilde{\vect{A}}^{r,*} \mathfrak{D}^r\tilde{\vect{A}}^r\\
 C_r &=\int_{\partial\mathcal{O}_r}d\vect{x}\,
 (\vect{K}^r\cdot\vect{L}^{E,r} + \vect{N}^r\cdot\vect{L}^{M,r})\cdot\tilde{\vect{A}}^r\\
 C_e&=\sum_{r}\int_{\partial\mathcal{O}_r}d\vect{x}\,
 (\vect{K}^r\cdot\vect{L}^{E,e} + \vect{N}^r\cdot\vect{L}^{M,e})\cdot\tilde{\vect{A}}^e
\end{align}
At this point, the integral over fields internal to the bodies $\tilde{\vect{A}}^r$, and fields 
external to all bodies, $\tilde{\vect{A}}^e$ is carried out.  The internal integral couples the currents
on the same body to one another, while the external integral couples currents on different bodies together.
The resulting path integral is
\begin{align}
  Z_{TE} &= \int \prod_rD\vect{K}_rD\vect{N}_re^{-S_e[\vect{K}_r,\vect{N}_r] - S_r[\vect{K}_r,\vect{N}_r] }
\end{align}
where the external and internal effective actions are given by 
\begin{align}
  S_e&:=\frac{1}{2\beta}\sum_{r,r'}
  \int\limits_{\partial\mathcal{O}_r}d\vect{x}\int\limits_{\partial\mathcal{O}_{r'}}d\vect{x'}\, 
  (\vect{K}^r\cdot\vect{L}^{E,e} + \vect{N}^r\cdot\vect{L}^{M,e})(x)\cdot\vect{G}^e\cdot
  (\vect{K}^{r'}\cdot\vect{L}^{E,e} + \vect{N}^{r'}\cdot\vect{L}^{M,e})(x')\\
  S_r&:= \frac{1}{2\beta}\sum_{r}\int_{\partial\mathcal{O}_r}d\vect{x}\int_{\partial\mathcal{O}_r}d\vect{x'}\,
    [\vect{K}^r\cdot\vect{L}^{E,r} + \vect{N}^r\cdot\vect{L}^{M,r}](x)\cdot
    \vect{G}^r\cdot[\vect{K}^r\cdot\vect{L}^{E,r} + \vect{N}^r\cdot\vect{L}^{M,r}](x')\bigg\}.
\end{align}
Note that the $S_r$ correspond to body self-energies, as do terms with $r=r'$ from $S_e$.
(Note you don't carry out renormalization yet - this is added to interaction terms.  WHen we compute
the determinant these do not cleanly decouple, thus you can't just throw this away.)

% Both of these correspond to photon exchange from patches on the same body.  
% These terms renormalize out if we consider energy differences between configurations where the 
% bodies are removed to spatial infinity.  These terms are independent of all other positioning
% of the bodies, and amount to additive constants to the action.  In the partition function
% they are multiplicative constants, $Z_{TE,r}$, where we can also use
% $ Z_{TE,\infty} = \prod_r Z_{TE,r}$, since there are no interactions between the bodies in this limit.
Focusing on the interaction terms, the effective interaction integrand of the path integral 
can be written as 
\begin{align}
  S_{e}[\vect{K},\vect{N}] &= \frac{1}{2\beta}\sum_{r\ne r'}
  \int\limits_{\partial\mathcal{O}_r}d\vect{x}\int\limits_{\partial\mathcal{O}_{r'}}d\vect{x'}\, 
\left(\hspace{-0.1cm} \begin{array}{cc} 
    \vect{K}^r(x) &   \vect{N}^r(x)
  \end{array}
\hspace{-0.1cm}
\right)
\left(\begin{array}{cc} 
    \vect{L}^{E,e}\vect{G}\vect{L}^{E,e} &\vect{L}^{E,e}\vect{G}\vect{L}^{M,e}\\
    \vect{L}^{M,e}\vect{G}\vect{L}^{E,e} &\vect{L}^{M,e}\vect{G}\vect{L}^{M,e}\\
  \end{array}
  \right)
\left(\hspace{-0.1cm} \begin{array}{c} 
    \vect{K}^{r'}(x') \\   \vect{N}^{r'}(x')
  \end{array}
\hspace{-0.1cm}
\right)
\end{align}
The corresponding interior term is replaces $L$ and $G$ with their interior equivalents.  

It turns out that the combined matrices $L^P G L^Q$ correspond exactly to the usual homogenous Green function
dyadics, $\Gamma^{PQ}$ for $P, Q\in\{E,M\}$.  In addition, the gauge-pieces do not contribute at all.  

First, we need the Green function $\mathbf{G}$ corresponding to $\mathcal{D} =\mathcal{D}_1-\mathcal{D}_2$.
Fortunately, give the projector structure this is easy to derive.  Recall that
\begin{align}
  \mathfrak{D} = \alpha^2[P_T +\alpha^{-1}_{FP}P_L]
\end{align}
where $\alpha_\mu=(i\sqrt{\epsilon}\xi,\frac{1}{\sqrt{\mu}}\nabla)$, and we introduced
the projection operators which the following properties
\begin{gather}
  P_L+P_T = I\\
  P_L = \frac{\alpha^\mu\alpha^\nu}{\alpha^2}\\
  P_T = \delta_{\mu\nu}-\frac{\alpha^\mu\alpha^\nu}{\alpha^2}.
\end{gather}
(Reid points out that manipulating these things is actually easiest in momentum space.  We can use
\begin{equation}
  \int d\vect{x} F(\vect{x})D(\partial_i)G(\vect{x}) = \int \frac{d\vect{q}}{(2\pi)^d}
  F(\vect{q})D(i q_j)G(-\vect{q}).
\end{equation}
Then we can find the Fourier-space green function using 
$\alpha(q) = i(\sqrt{\epsilon}\xi,\frac{\vect{q}}{\sqrt{\mu}})$
\begin{align}
  I &=\mathfrak{D}G \\
  &=\alpha^2[P_T -\alpha^{-1}_{FP}P_L](a G_T+bG_L)\\
  \rightarrow \vect{G}& = \frac{1}{\alpha^2}(P_T - \alpha_{FP}P_L)
   = -\frac{\mu_r}{\kappa^2+\vect{q}^2}[\delta^{\mu\nu}
  + \frac{\mu_r(1-\alpha_{FP})}{\kappa^2+\vect{q}^2}\alpha^\mu\alpha^\nu],
\end{align}
where we used $\alpha^2 = -\epsilon_r\mu_r\xi^2-\vect{q}^2$,  and defined 
$\kappa = \sqrt{\epsilon\mu}\xi$.
None of the longitudinal components of $\alpha^\mu\alpha^\nu$ contribute to the path 
integral, since under the appropriate differentiation, they all vanish.  

% \subsubsection{Nasty-Nasty working-1}

% We can do this in two steps.  
% Notethat $P_L$ is a purely longitudinal/gauge degree of freedom.  The $L$ operators 
% convert from potentials to physical fields.  Thus we expect $L^P_{j\mu} \alpha^\mu=0$.

% Let's verify that for E and then $M$
% \begin{align}
%   L^{E,r}_{i\nu}\alpha^\nu\sqrt{\mu_r} = -i\left( \begin{array}{cccc} 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_x & -\xi & 0 & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_y & 0 &-\xi & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_z & 0 & 0 & -\xi
%     \end{array}
%   \right)
%   \left(\begin{array}{c}
%       \sqrt{\epsilon_r\mu_r} \xi \\        q_x \\        q_y\\        q_z
%       \end{array}
%     \right) = \vect{0}
%   \end{align}
% Similarly,
% \begin{align}
%   L^{M,r}_{i\nu}\alpha^\nu\sqrt{\mu_r} = -
%    \frac{1}{\mu_r}\left( \begin{array}{cccc} 
%       0 & 0 & -q_z & q_y\\
%       0 & q_z & 0 & -q_x\\
%       0 & -q_y & q_x & 0
%     \end{array}
%   \right)
%   \left(\begin{array}{c}
%       \sqrt{\epsilon_r\mu_r} \xi \\        q_x \\        q_y\\        q_z
%       \end{array}
%     \right) = \vect{0}
%   \end{align}
% The actual matrix products correspond to outer-products of pairs of these, and they are all zero.

% The non-zero products involve a middle identity tensor.  The remaining products require 
% the products between various $L$ matrices.
% First Electric-Electric
% \begin{align}
%   L^{E,r}_{i\nu}L^{E,r}_{j\nu}&=
%  -\left( \begin{array}{cccc} 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_x & -\xi & 0 & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_y & 0 &-\xi & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_z & 0 & 0 & -\xi
%     \end{array}
%   \right)
% \left( \begin{array}{ccc} 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_x & \frac{1}{\sqrt{\epsilon^r\mu^r}}q_y & 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_z\\
%       -\xi &0 & 0\\
%        0   &-\xi & 0\\
%        0   & 0 & -\xi
%     \end{array}
%   \right)\\
% &=-\xi^2\delta_{ij}-c^2q_iq_j
% \end{align}
% Second, Magnetic-Magnetic
% \begin{align}
%   L^{M,r}_{i\nu}L^{M,r}_{j\nu} &= -
%    \frac{1}{\mu_r^2}\left( \begin{array}{cccc} 
%       0 & 0 & -q_z & q_y\\
%       0 & q_z & 0 & -q_x\\
%       0 & -q_y & q_x & 0
%     \end{array}
%   \right)
% \left( \begin{array}{cccc} 
%       0 & 0 &  0\\
%       0 & q_z & -q_y\\
%       -q_z & 0 & q_x\\
%       q_y & -q_x & 0
%     \end{array}
%   \right)\\
% &=\frac{1}{\mu_r^2}(\vect{q}^2\delta_{ij}-q_iq_j)
% \end{align}
% Finally Electric-Magnetic
% \begin{align}
%   L^{M,r}_{i\nu}L^{M,r}_{j\nu} &= -
%    \frac{1}{\mu_r}
%  \left( \begin{array}{cccc} 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_x & -\xi & 0 & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_y & 0 &-\xi & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_z & 0 & 0 & -\xi
%     \end{array}
%   \right)
% \left( \begin{array}{cccc} 
%       0 & 0 &  0\\
%       0 & q_z & -q_y\\
%       -q_z & 0 & q_x\\
%       q_y & -q_x & 0
%     \end{array}
%   \right)\\
% &=-\frac{\xi}{\mu_r} \left( \begin{array}{ccc} 
%       0 & q_z & -q_y\\
%       -q_z & 0 & q_x\\
%       q_y & -q_x & 0
%     \end{array}
%   \right)
% \end{align}

% (Should probably skip most of this - note differing methods, approximations, and rough technique.)
% But it does suggest a useful comparison for worldline.  




% \subsection{Reid 2013}

% \subsubsection{Intro}

% Interaction of effective currents on surfaces.  Get energies/forces/torques from
% this matrix, and appropriate derivatives.  Derive things two ways:
% i) stress-tensor, ii) path-integral expression.  Get to the same place both ways.  

% Point out derivation holds for general temperatures, cite Philbin and Pitaevskii
% as pointing out doubts about the canonical case.  

% Note use of special function methods that work great when well-suited basis is 
% available.  (Cites Lambrecht, Kenneth/Klich here and others.)

% Then note Maxwell stress-tensor approach requires integral over volume.
% Reid2013 eliminates the volume integral for a surface integral, where surface currents
% enter as fixing EM boundary conditions on some bounding surface.    

% The basic formulae are: 
% \begin{gather}
%   \mathcal{E} = \frac{\hbar}{2\pi}\int_0^\infty d\xi \ln\frac{\det\mathbf{M}(\xi)}{\det\mathbf{M}_\infty(\xi)}
%   \quad \text{(T=0 energy density)}\\
%   \mathcal{F}_i = -\frac{\hbar}{2\pi}\int_0^\infty d\xi \tr\left[\mathbf{M}^{-1}(\xi)
% \frac{\partial}{\partial \vect{r}_i}\mathbf{M}(\xi)\right]\quad \text{(T=0 Force)}\\
%   \mathcal{T}_i = -\frac{\hbar}{2\pi}\int_0^\infty d\xi \tr\left[\mathbf{M}^{-1}(\xi)
% \frac{\partial}{\partial \theta_i}\mathbf{M}(\xi)\right]\quad \text{(T=0 Torque)}
% \end{gather}
% $\xi$ Integrals run over imaginary axis.  Trace runs over all scattering matrix elements.  
% Similarity to Rahi work in the matrices.  The meaning however is coupling/scattering between
% different bases.  Here it is coupling between surface current elementss.  There it was 
% between different field modes.  

% Point out their method is more general than mode-function version, 
% and better adapted when basis is not good.

% Can also use coupling between Homogenous Green functions (re Stratton, and Emig2004 ).

% This paper is theoretical - numerical details discussed elsewhere. 


% \subsection{Path Integral Derivation}

% Do gauge-fixing method of quantization of path integral.
% Assuming linear coupling, at zero temperature.  

% In contrast with taking ``Weyl gauge'' $A_0=0$, or in terms of Electric fields.    

% Introduce surface currents via fixing EM boundary conditions on surfaces.  

% (Cites a 1985 Bordag Ann. Phys Paper for similarities explicit independence of Fadeev-Popov
% gauge fixing).

% The action is 
% \begin{equation}
%   S = \frac{1}{2}\int\frac{d\omega}{2\pi}\int d^3x\,\left[ 
%     \epsilon(\omega,\vect{x})|\vect{E}(\omega,\vect{x})|^2 - \mu(\omega,\vect{x})|\vect{H}(\omega,\vect{x})|^2\right]
% \end{equation}
% Then rewriting $\vect{E},\vect{H}$ in terms of the 4-potentials, the initial Lagrangian density is 
% \begin{equation}
%  \mathcal{L}= \int\frac{1}{2}\int\frac{d\omega}{2\pi}\,\left[ 
%     \epsilon(\omega,\vect{x})(\partial_i A^0+i\omega A^i)(\partial_i {A^0}^*-i\omega A^i)
% - \frac{1}{\mu}(\epsilon_{ijk}\partial_jA^k\epsilon_{imn}\partial_mA^n)\right]
% \end{equation}
% \begin{shaded}
% This follows since if we Fourier expand the real-valued time version of this we have 
% \begin{equation}
%   \int_{0}^T dt e^{i(\omega_n+\omega_mt)}A_nA_m = A_nA_m^*\delta_{n,-m}
% \end{equation}
% Since the fields are real, $A_n^* = A_{-n}$.  If we take the limit $T\rightarrow\infty$,
% the Fourier series is replaced by a sum.  (This will recur again when we confront finite temperature.)
% \end{shaded}
% Now integrate by parts, and Wick rotate to Euclidean space with 
% $\{\omega, A^0, {A^0}^*\}\rightarrow \{i\xi,iA_0,iA_0^*\}$.
% \begin{align}
%  \mathcal{L}&= \int\frac{1}{2}\int\frac{d\omega}{2\pi}\,\big[ 
%     \epsilon(\omega,\vect{x})(\partial_i A^0\partial_i {A^0}^*+i\omega A^i\partial_i {A^0}^*
%     -i\omega\partial_iA^0{A^i}^* +\omega^2A^i {A^i}^*)\nonumber\\
%     &- \frac{1}{\mu}(\partial_jA^k\partial_jA^k-\partial_jA^k\partial_kA^j)\big]\\
% % &= \int\frac{1}{2}\int\frac{d\omega}{2\pi}\,\big[ 
% %     \epsilon(\omega,\vect{x})( A^0(-\partial_i\partial^i) {A^0}^*+i\omega A^i\partial_i {A^0}^*
% %     -i\omega\partial_iA^0{A^i}^*+\omega^2A^i {A^i}^*)\nonumber\\
% %     &+ \frac{1}{\mu}(A^k\partial_j\partial_jA^k-A^k\partial_j\partial_kA^j) 
% %     -A^0(\partial_i\epsilon)\partial_iA^{0*} +A^k(\partial_j\frac{1}{\mu})(\partial_jA^k-\partial_kA^j)\big]
% &= \int\frac{1}{2}\int\frac{d\omega}{2\pi}\,\big[ 
%     \epsilon(\omega,\vect{x})( A^{0,*}(-\partial_i\partial^i) A^0-i\omega {A^0}^*(\partial_iA^i+A^i\partial_i\epsilon)
%     -i\omega\partial_iA^0{A^i}^*+\omega^2A^i {A^i}^*)\nonumber\\
%     &+ \frac{1}{\mu}(A^k\partial_j\partial_jA^k-A^k\partial_j\partial_kA^j) 
%     -A^0(\partial_i\epsilon)\partial_iA^{0*} +A^k(\partial_j\frac{1}{\mu})(\partial_jA^k-\partial_kA^j)\big]
% \end{align}
% \begin{shaded}
% \comment{Wait - WTF?  They dropped any terms like $\partial_i\epsilon A^i A^0$.  Is this part of 
% assuming $\epsilon$ is piecewise constant, and thus these terms occur on the surfaces anyway?
% Since they will explicitly fix the fields on the boundary regions to satisfy Maxwell's equations, 
% they can omit these pieces? Or would these pieces act as effective boundary conditions?}
% \end{shaded}
% Then split the Lagrangian into: 
% \begin{equation}
%   \mathcal{L}=\tilde{A}^{\mu,*} [\left(-\epsilon\xi^2+\frac{1}{\mu}\nabla^2\right)\delta_{\mu\nu} 
%   - \alpha_\mu\alpha_\nu]\tilde{A}^\nu,
% \end{equation}
% where $(\tilde{A}^0,\tilde{A}^j) = (\sqrt{\epsilon\mu}A^0,\vect{A})$, 
% and $\alpha_\mu=(i\sqrt{\epsilon}\xi,\frac{1}{\sqrt{\mu}}\nabla)$.
% We can equivalently write this as 
% \begin{equation}
%   \mathcal{L}=\tilde{A}^{\mu,*} [\alpha_\rho\alpha^\rho\delta_{\mu\nu} - \alpha_\mu\alpha_\nu]\tilde{A}^\nu,
% \end{equation}
% which transparently has the form of a transverse projector.  
% This has a null eigenvalue along $\alpha_\mu$, which corresponds to gauge-transformations.  
% The null eigenvalue is normally removed within path integrals by using the Fadeev-Popov method for gauge fixing. 
% While Fadeev-Popov gauge fixing runs into issues in Non-Abelian theories at very large field strengths,
% we are only going to use it for perturbative QED computations, well inside its range of validity.
% They then link up with the Fadeev-Popov
% method by noting that the Fadeev-Popov method handles gauge-fixing by introducing 
% \begin{equation}
%   1 = \int d\omega \exp\left[-\int_0^{\hbar\beta}d\tau\,\frac{\omega^2}{2} \right]
%   \det[-\frac{\delta G}{\delta f}]\delta[G(a,f)-\omega]
% \end{equation}
% Here we have constructed two factors of unity.  First, we want to eliminate gauge degrees of freedom
% by fixing $G(a)=0$, via a functional delta function.  We must include the leading determinant
% to account to give the correct weight to each physically independent state.
% Secondly we use t'Hooft's trick of displacing the gauge fixing to $\omega$, which we integrate over.

% If we use a generalized Lorentz gauge 
% \begin{equation}
%   G[\tilde{A}^0,\tilde{A}^j] = i\omega \tilde{A}^0 + \partial_j \tilde{A}^j,
% \end{equation}
% then under the gauge transformation
% \begin{equation}
%   (\tilde{A}^0,A^j)\rightarrow  (\tilde{A}^0,A^j) + (i\omega,\partial^j)f,
% \end{equation}
% we can find the functional derivative, 
% \begin{equation}
%   \frac{\delta G}{\delta f} = \frac{G[A^0+i\omega f,A^j+\partial^jf]  -[A^0,A^j]}{f}
%   = (-\omega^2 +\partial_j^2)
% \end{equation}
% Note that framed in these variables the are no boundary terms at discontinuities.  
% This functional determinant is constant, and does not depend on the geometry at all.  

% The gauge-fixed Lagrangian is given by
% \begin{equation}
%   \mathcal{L}=\tilde{A}^{\mu,*} [\alpha_\rho\alpha^\rho\delta_{\mu\nu}
%   -(1-\alpha^{-1}_{FP})\alpha_\mu\alpha_\nu]\tilde{A}^\nu
% =\tilde{\vect{A}}^{*}[\mathfrak{D}_1-\mathfrak{D}_2]\tilde{\vect{A}},
% \end{equation}
% where $\alpha_{FP}=1$ corresponds to so-called Feynman gauge, and $\alpha_{FP}=\infty$ is Landau gauge.
% Note that this derivation proceeds under the assumption that we will  explicitly enforce 
% EM boundary conditions at all surfaces.  Thus we can neglect and ignore any terms involving
% $\partial_i\epsilon$.   This stands in contrast to our approach which would attempt to retain 
% all such terms.  Our attempts at this path integral for the worldline method would retain these
% terms to enforce boundary conditions, and to scale the gradients to be in flat space.  

% The claim is that the partition function is given by 
% \begin{equation}
%   Z_{EM} = \int [D\tilde{A}]_C e^{-\frac{\beta}{2}\int d\vect{x} \mathcal{L}},
% \end{equation}
% where $[D\tilde{A}]_C$ integrates over all field conditions that satisfy the boundary conditions.
% The boundary conditions will be explicitly enforced via functional delta-functions.  

% \subsubsection{EM Boundary Conditions}

% At a surface the tangential electric and magnetic fields are continuous.

% Recall that Maxwell's equations in media are:
% \begin{gather}
%   \nabla\times \vect{E} =-\partial_t \vect{B}\\
%   \nabla\cdot\vect{B}=0\\
%   \nabla\times\vect{H} = -\partial_t \vect{D} +\vect{j}\\
%   \nabla\cdot\vect{D} =\rho.
% \end{gather}
% If we use the integral forms of these equations we can derive the EM boundary conditions.
% We assume we are working without sources, other than the bound charges on the objects.  

% Then with appropriate Gaussian pillboxes, and Stokes' loops we have:
% \begin{gather}
%   \vect{E}^\|_1 =\vect{E}^\|_2 \\
%   B_1^\perp = B_2^\perp\\
%   \vect{H}^\|_1 =\vect{H}^\|_2 \\
%   D_1^\perp = D_2^\perp,
% \end{gather}
% where the $1,2$ subscripts denote the media the fields are evaluated in.  
% We can enforce boundary conditions in path integrals via functional delta functions using
% the Fourier representation of the delta function 
% (Cites Bordag, and Kardar and Li)
% \begin{equation}
%   \delta(\vect{E}^\|_1-\vect{E}^\|_2) = \int D\vect{K} e^{i\int_{\partial \mathcal{O}} d^3\vect{x}\,
%     \vect{K}\cdot(\vect{E}^\|_1-\vect{E}^\|_2)},
% \end{equation}
% where the integral takes place over the interface/boundary of the object $\mathcal{O}$.
% There is a similar expression for the magnetic fields $\vect{H}$, with $\vect{N}$ as the multiplier.  
% These Lagrange multiplier fields correspond to the fluctuating surface currents, as they 
% are just the currents one must have to enforce the boundary conditions.  

% The boundary conditions can be recast in terms of the gauge fields by introducing an appropriate
% derivative operators $L^{E,r}$ and $L^{M,r}$.  In piece-wise constant media the operators are given by
% \begin{equation}
%   E_j:=L^{E,r}_{j\mu}\tilde{A}^\mu = -\frac{1}{\sqrt{\epsilon^r\mu^r}}\partial_j \tilde{A}^0+i\xi A^j
%   H_j:=L^{M,r}_{j\mu}\tilde{A}^\mu = \frac{1}{\mu^r}\epsilon_{jkl}\partial_k A^l
% \end{equation}
% In matrix form
% \begin{gather}
%   L^{E,r} = \left( \begin{array}{cccc} 
%       -\frac{1}{\sqrt{\epsilon^r\mu^r}}\partial_x & i\xi & 0 & 0\\
%       -\frac{1}{\sqrt{\epsilon^r\mu^r}}\partial_y & 0 &i\xi & 0\\
%       -\frac{1}{\sqrt{\epsilon^r\mu^r}}\partial_z & 0 & 0 & i\xi
%     \end{array}
%   \right)\\
%   L^{M,r} = \frac{1}{\mu_r}\left( \begin{array}{cccc} 
%       0 & 0 & -\partial_z & \partial_y\\
%       0 & \partial_z & 0 & -\partial_x\\
%       0 & -\partial_y & \partial_x & 0
%     \end{array}
%   \right)
%   \end{gather}
% Note that the piece-wise continuous media assumption lets you commute derivatives and 
% material functions with impunity. 

% \subsubsection{Integrating out the photon field}

% We can now insert the functional delta functions to create the constrained path-integral.  
% It is then a relatively straightforward matter of integrating out the photon 4-vector field.  
% This will leave us with a picture of interacting surface currents.  
% \begin{align}
%   Z_{TE} &= \int D\tilde{A}^\mu \prod_rD\vect{K}_rD\vect{N}_r\exp\bigg\{-\frac{\beta}{2}\int d^3\vect{x}\,
%     \tilde{\vect{A}}^{*} [\mathfrak{D}_1 -\mathfrak{D}_2]\tilde{\vect{A}}\nonumber\\
%     &\hspace{1cm}  +i\sum_{r} \int_{\partial\mathcal{O}_r}d\vect{x}\,\vect{K}\cdot(
%     \vect{L}^{E,r}\tilde{\vect{A}}^{r}-\vect{L}^{E,e}\tilde{\vect{A}}^e)\nonumber\\
%     &\hspace{1cm}  +i\sum_{r} \int_{\partial\mathcal{O}_r}d\vect{x}\,\vect{N}\cdot(
%     \vect{L}^{M,r}\tilde{\vect{A}}^{r}-\vect{L}^{M,e}\tilde{\vect{A}}^e)\bigg\}
% \end{align}
% where we use $r$ to denote the body at position $\vect{x}$, and $e$ to denote the exterior.
% Note that both the operators, and fields depend on material constants, resulting in a somewhat
% overburdened notation.  We have introduced bold-face to denote both vectors and matrices.

% We are then free to evaluate the Gaussian integral over $\vect{A}$ in each region, using
% \begin{equation}
%   \int D\phi e^{-\frac{\beta}{2}\int d^3\vect{x}\, [\phi^i \mathcal{L}_{ij}\phi^j +i+\psi^k\phi_k]}
% = e^{-\frac{1}{2\beta}\int d^3\vect{x}\,\psi^k G_{km} \psi^m},
% \end{equation}
% where $\mathcal{L}_{ij}G^{jm} = \delta_{i}^m$, and $G$ is the Green function corresponding to $L$.
% The partition function can be slightly re-arranged to a more suitable form,
% \begin{align}
%   Z_{TE} &= \int D\tilde{A}^\mu \prod_rD\vect{K}_rD\vect{N}_re^{-S_{A,e}-\sum_rS_{A,r}+i\sum_rC_r-iC_e}
% \end{align}
% where 
% \begin{align}
%   S_{A,e}&=\frac{\beta}{2}\int_e d^3\vect{x}\,  \tilde{\vect{A}}^{e,*} \mathfrak{D}^e\tilde{\vect{A}}^e \\
%  S_{A,r}&=\frac{\beta}{2}\int_r d^3\vect{x}\, \tilde{\vect{A}}^{r,*} \mathfrak{D}^r\tilde{\vect{A}}^r\\
%  C_r &=\int_{\partial\mathcal{O}_r}d\vect{x}\,
%  (\vect{K}^r\cdot\vect{L}^{E,r} + \vect{N}^r\cdot\vect{L}^{M,r})\cdot\tilde{\vect{A}}^r\\
%  C_e&=\sum_{r}\int_{\partial\mathcal{O}_r}d\vect{x}\,
%  (\vect{K}^r\cdot\vect{L}^{E,e} + \vect{N}^r\cdot\vect{L}^{M,e})\cdot\tilde{\vect{A}}^e
% \end{align}
% If we integrate out the fields on body $\mathcal{O}_r$, and then over the exterior fields then
% \begin{align}
%   Z_{TE} &= \int \prod_rD\vect{K}_rD\vect{N}_re^{-S_e[\vect{K}_r,\vect{N}_r] - S_r[\vect{K}_r,\vect{N}_r] }
% \end{align}
% where the external and internal effective actions are given by 
% \begin{align}
%   S_e&:=\frac{1}{2\beta}\sum_{r,r'}
%   \int\limits_{\partial\mathcal{O}_r}d\vect{x}\int\limits_{\partial\mathcal{O}_{r'}}d\vect{x'}\, 
%   (\vect{K}^r\cdot\vect{L}^{E,e} + \vect{N}^r\cdot\vect{L}^{M,e})(x)\cdot\vect{G}^e\cdot
%   (\vect{K}^{r'}\cdot\vect{L}^{E,e} + \vect{N}^{r'}\cdot\vect{L}^{M,e})(x')\\
%   S_r&:= \frac{1}{2\beta}\sum_{r}\int_{\partial\mathcal{O}_r}d\vect{x}\int_{\partial\mathcal{O}_r}d\vect{x'}\,
%     [\vect{K}^r\cdot\vect{L}^{E,r} + \vect{N}^r\cdot\vect{L}^{M,r}](x)\cdot
%     \vect{G}^r\cdot[\vect{K}^r\cdot\vect{L}^{E,r} + \vect{N}^r\cdot\vect{L}^{M,r}](x')\bigg\}.
% \end{align}
% Note that the $S_r$ correspond to body self-energies, as do terms with $r=r'$ from $S_e$.
% (Note you don't carry out renormalization yet - this is added to interaction terms.  WHen we compute
% the determinant these do not cleanly decouple, thus you can't just throw this away.)

% % Both of these correspond to photon exchange from patches on the same body.  
% % These terms renormalize out if we consider energy differences between configurations where the 
% % bodies are removed to spatial infinity.  These terms are independent of all other positioning
% % of the bodies, and amount to additive constants to the action.  In the partition function
% % they are multiplicative constants, $Z_{TE,r}$, where we can also use
% % $ Z_{TE,\infty} = \prod_r Z_{TE,r}$, since there are no interactions between the bodies in this limit.
% Focusing on the interaction terms, the effective interaction integrand of the path integral 
% can be written as 
% \begin{align}
%   S_{e}[\vect{K},\vect{N}] &= \frac{1}{2\beta}\sum_{r\ne r'}
%   \int\limits_{\partial\mathcal{O}_r}d\vect{x}\int\limits_{\partial\mathcal{O}_{r'}}d\vect{x'}\, 
% \left(\hspace{-0.1cm} \begin{array}{cc} 
%     \vect{K}^r(x) &   \vect{N}^r(x)
%   \end{array}
% \hspace{-0.1cm}
% \right)
% \left(\begin{array}{cc} 
%     \vect{L}^{E,e}\vect{G}\vect{L}^{E,e} &\vect{L}^{E,e}\vect{G}\vect{L}^{M,e}\\
%     \vect{L}^{M,e}\vect{G}\vect{L}^{E,e} &\vect{L}^{M,e}\vect{G}\vect{L}^{M,e}\\
%   \end{array}
%   \right)
% \left(\hspace{-0.1cm} \begin{array}{c} 
%     \vect{K}^{r'}(x') \\   \vect{N}^{r'}(x')
%   \end{array}
% \hspace{-0.1cm}
% \right)
% \end{align}
% The corresponding interior term is replaces $L$ and $G$ with their interior equivalents.  

% It turns out that the combined matrices $L^P G L^Q$ correspond exactly to the usual homogenous Green function
% dyadics, $\Gamma^{PQ}$ for $P, Q\in\{E,M\}$.  In addition, the gauge-pieces do not contribute at all.  

% First, we need the Green function $\mathbf{G}$ corresponding to $\mathcal{D} =\mathcal{D}_1-\mathcal{D}_2$.
% Fortunately, give the projector structure this is easy to derive.  Recall that
% \begin{align}
%   \mathfrak{D} = \alpha^2[P_T +\alpha^{-1}_{FP}P_L]
% \end{align}
% where $\alpha_\mu=(i\sqrt{\epsilon}\xi,\frac{1}{\sqrt{\mu}}\nabla)$, and we introduced
% the projection operators which the following properties
% \begin{gather}
%   P_L+P_T = I\\
%   P_L = \frac{\alpha^\mu\alpha^\nu}{\alpha^2}\\
%   P_T = \delta_{\mu\nu}-\frac{\alpha^\mu\alpha^\nu}{\alpha^2}.
% \end{gather}
% (Reid points out that manipulating these things is actually easiest in momentum space.  We can use
% \begin{equation}
%   \int d\vect{x} F(\vect{x})D(\partial_i)G(\vect{x}) = \int \frac{d\vect{q}}{(2\pi)^d}
%   F(\vect{q})D(i q_j)G(-\vect{q}).
% \end{equation}
% Then we can find the Fourier-space green function using 
% $\alpha(q) = i(\sqrt{\epsilon}\xi,\frac{\vect{q}}{\sqrt{\mu}})$
% \begin{align}
%   I &=\mathfrak{D}G \\
%   &=\alpha^2[P_T -\alpha^{-1}_{FP}P_L](a G_T+bG_L)\\
%   \rightarrow \vect{G}& = \frac{1}{\alpha^2}(P_T - \alpha_{FP}P_L)
%    = -\frac{\mu_r}{\kappa^2+\vect{q}^2}[\delta^{\mu\nu}
%   + \frac{\mu_r(1-\alpha_{FP})}{\kappa^2+\vect{q}^2}\alpha^\mu\alpha^\nu],
% \end{align}
% where we used $\alpha^2 = -\epsilon_r\mu_r\xi^2-\vect{q}^2$,  and defined 
% $\kappa = \sqrt{\epsilon\mu}\xi$.
% Reid claims that the second longitudinal term does not contribute at all, and thus the 
% gauge-fixing does not affect anything.  

% \subsubsection{Nasty-Nasty working-1}

% We can do this in two steps.  
% Notethat $P_L$ is a purely longitudinal/gauge degree of freedom.  The $L$ operators 
% convert from potentials to physical fields.  Thus we expect $L^P_{j\mu} \alpha^\mu=0$.

% Let's verify that for E and then $M$
% \begin{align}
%   L^{E,r}_{i\nu}\alpha^\nu\sqrt{\mu_r} = -i\left( \begin{array}{cccc} 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_x & -\xi & 0 & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_y & 0 &-\xi & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_z & 0 & 0 & -\xi
%     \end{array}
%   \right)
%   \left(\begin{array}{c}
%       \sqrt{\epsilon_r\mu_r} \xi \\        q_x \\        q_y\\        q_z
%       \end{array}
%     \right) = \vect{0}
%   \end{align}
% Similarly,
% \begin{align}
%   L^{M,r}_{i\nu}\alpha^\nu\sqrt{\mu_r} = -
%    \frac{1}{\mu_r}\left( \begin{array}{cccc} 
%       0 & 0 & -q_z & q_y\\
%       0 & q_z & 0 & -q_x\\
%       0 & -q_y & q_x & 0
%     \end{array}
%   \right)
%   \left(\begin{array}{c}
%       \sqrt{\epsilon_r\mu_r} \xi \\        q_x \\        q_y\\        q_z
%       \end{array}
%     \right) = \vect{0}
%   \end{align}
% The actual matrix products correspond to outer-products of pairs of these, and they are all zero.

% The non-zero products involve a middle identity tensor.  The remaining products require 
% the products between various $L$ matrices.
% First Electric-Electric
% \begin{align}
%   L^{E,r}_{i\nu}L^{E,r}_{j\nu}&=
%  -\left( \begin{array}{cccc} 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_x & -\xi & 0 & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_y & 0 &-\xi & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_z & 0 & 0 & -\xi
%     \end{array}
%   \right)
% \left( \begin{array}{ccc} 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_x & \frac{1}{\sqrt{\epsilon^r\mu^r}}q_y & 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_z\\
%       -\xi &0 & 0\\
%        0   &-\xi & 0\\
%        0   & 0 & -\xi
%     \end{array}
%   \right)\\
% &=-\xi^2\delta_{ij}-c^2q_iq_j
% \end{align}
% Second, Magnetic-Magnetic
% \begin{align}
%   L^{M,r}_{i\nu}L^{M,r}_{j\nu} &= -
%    \frac{1}{\mu_r^2}\left( \begin{array}{cccc} 
%       0 & 0 & -q_z & q_y\\
%       0 & q_z & 0 & -q_x\\
%       0 & -q_y & q_x & 0
%     \end{array}
%   \right)
% \left( \begin{array}{cccc} 
%       0 & 0 &  0\\
%       0 & q_z & -q_y\\
%       -q_z & 0 & q_x\\
%       q_y & -q_x & 0
%     \end{array}
%   \right)\\
% &=\frac{1}{\mu_r^2}(\vect{q}^2\delta_{ij}-q_iq_j)
% \end{align}
% Finally Electric-Magnetic
% \begin{align}
%   L^{M,r}_{i\nu}L^{M,r}_{j\nu} &= -
%    \frac{1}{\mu_r}
%  \left( \begin{array}{cccc} 
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_x & -\xi & 0 & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_y & 0 &-\xi & 0\\
%       \frac{1}{\sqrt{\epsilon^r\mu^r}}q_z & 0 & 0 & -\xi
%     \end{array}
%   \right)
% \left( \begin{array}{cccc} 
%       0 & 0 &  0\\
%       0 & q_z & -q_y\\
%       -q_z & 0 & q_x\\
%       q_y & -q_x & 0
%     \end{array}
%   \right)\\
% &=-\frac{\xi}{\mu_r} \left( \begin{array}{ccc} 
%       0 & q_z & -q_y\\
%       -q_z & 0 & q_x\\
%       q_y & -q_x & 0
%     \end{array}
%   \right)
% \end{align}

% (Should probably skip most of this - note differing methods, approximations, and rough technique.)
% But it does suggest a useful comparison for worldline.  




\section{Repulsion}

\begin{itemize}
\item Cite Milton paper on anisotropy \cite{Milton2012, Milton2012a}
\item Cite work on metamaterials (hydrogen mirror)
\item Cite Milonni/rosa showing broad-band \cite{Rosa2010}
\end{itemize}

\section{Papers: Worldlines}

Note citations in Bordag/Johnson mostly as dismissive and limited.  

\subsection{Effective actions}

\cite{McKeon1993, Strassler1992,Schubert2001}

\comment{Other references - was one contemporaneous with Strassler? Bern-Kosower}

\comment{Cite 1950 Feynman Scalar QED section}

\cite{Schubert2001}.  

\subsubsection{Applied to QED}

For example, the worldline method has been used to compute relativistic field effects for QED such
 as the Lamb shift~\cite{Schmidt1995}.  It has also been used as a numerical algorithm\cite{Mazur2014}.

\subsection{Feynman Path Integral for QM}

\cite{Feynman1948,Feynman1965,Brown2005}.

\subsection{Papers: Gies Worldline}

\subsubsection{Gies 2003}
\cite{Gies2003}

\begin{itemize}
\item Cite earlier paper by themselves for first worldline numerics?   Found citations for PFA.
\item Action for scalar fields.   Massive scalar field interacting with some potential $V(x)$.
  $V$ has dimensions of mass-squared.  (Field theory units $\hbar=c=1$, so $E=mc^2$)
\begin{equation}
\cL = \frac{1}{2}\partial_\mu\phi\partial^\mu\phi +\frac{1}{2}m^2\phi^2+\frac{1}{2}V(x)\phi^2
\end{equation}
\item Complete unrenormalized quantum effective action for $V$ (integrate out fields $\phi$) is 
\begin{align}
  \Gamma[V] &=\frac{1}{2}\tr\ln \left[ \frac{-\partial_\mu\partial^\mu +m^2 + V(x)}
    {-\partial_\mu\partial^\mu +m^2}\right]\\
&   =-\frac{1}{2}\int \frac{d\cT}{\cT} \int d^D x \left\{ 
\langle x|e^{-\cT[-\partial_\mu\partial^\mu +m^2 + V(x)]}|x\rangle -\frac{e^{-m^2 \cT}}{(4\pi \cT)^{D/2}}\right\}
\end{align}
Working in $D=d+1$ euclidean space-time dimensions.  
\item Convert matrix element to path integral.  
\begin{equation}
  \int d^D x \langle x|e^{-\cT[-\partial^2+V(x)]}|x\rangle = \int d^D x_{\text{CM}} \mathcal{N}\int_{x(0)=x(\cT)}Dx e^{-\int_0^\cT d\tau \dot{x}^2/4}
\end{equation}
Comments: Fix normalization from limit of zero potential (which is evaluated in momentum basis), and note that choice to drop factors of 2 has left them with an extra $\sqrt{2}$ in the definition  of the loops.
\begin{align}
\langle x| e^{\partial^2T}|x\rangle &= \int d^Dp\frac{1}{(2\pi)^{D/2}} e^{-p^2T}\langle x|p\rangle\langle p|x\rangle\\
&= \frac{1}{(4\pi \cT)^{D/2}}\\
&=\cN \int_{x(0)=x(\cT)}Dx \exp\left\{-\int_0^\cT d\tau \left[\frac{\dot{x}^2}{4}+V(x_{\text{CM}}+x(\tau)\right]\right\}
\end{align}
\item Now interpret path integral as Gaussian integral/ensemble average over closed loops.  
\begin{equation}
\cN \int_{x(0)=x(\cT)}Dx \exp\left\{-\int_0^\cT d\tau \left[\frac{\dot{x}^2}{4}+V(x_{\text{CM}}+x(\tau)\right]\right\} = \frac{1}{(4\pi \cT)^{D/2}}\dlangle e^{-\int_0^\cT d\tau V[x_{\text{CM}}+x(\tau)]}\drangle
\end{equation}
Also use scaled loops: 
\begin{equation}
x_\mu(\cT t) = \sqrt{\cT}y_\mu(t),
\end{equation}
where $t\in [0,1]$, and we view $\cT$ as a parameter.  
\item Plugging in path representation
\begin{align}
\Gamma[V]=&-\frac{1}{2 (4\pi)^{D/2}}\int_{1/\Lambda^2}^\infty \frac{d\cT}{\cT^{1+D/2}} e^{-m^2\cT}\int d^Dx_{\text{CM}} \\
&\times\dlangle e^{-\cT\int_0^1dt V[x_\text{CM} +\sqrt{\cT}y(t)]}-1 \drangle
\end{align}
For time independent backgrounds use $\int dx_0 = L_{x_0}$ as ``length'' in time direction.  \comment{For partition function version Get $\beta\hbar c$ instead.}
\item \textbf{Renormalization}
Consider field theoretic renormalization (I think whereby an analogue of the Integral Trajectory Matching formalism fixes the unknown(divergent) values at some known scale - typically from a low energy experiment).  
\item Heat Kernel Expansion \comment{Cite Gilkey} .  Expand to non-diverging order to regularize UV divergences.  Each power of $V$ amounts to an external leg.  Get a Tadpole $T^{-D/2}\int dx_0 V$, and 
\item Ignore self-energies and focus on interaction energies (which are insentitive to Field theoretic divergence)
\begin{equation}
E_\text{int}= E_{V_1+V_2+\cdots}- E_{V_1} - E_{V_2}-\cdots
\end{equation}
Can carry out renormalization at loop level and thus avoid divergent sums.  
\item They note that this emphasis on interaction energy is \emph{not} a renormalization procedure.  It circumvents that for multiple bodies.  However for isolated bodies (sphere self-stress), one must specify all of the renormalization conditions, and your answers may depend on the procedure used.
\item \textbf{Numerics}
Introduce some methods (most of which are useless).
Important method is the v-loop.  An exact diagonalization of the Gaussians, under the loop closure constraint.  Note that they choose their loop constraint to be $\int d\tau y_\mu(\tau) =0$.  This amounts to making the center of mass of the loop centered on $x_\text{CM}$.  In contrast, our work has typically used $x(0)=x(\cT)=0$.  

The ``v-loop'' algorithm amounts to considering the probability measure,
\begin{equation}
P(\{x_k\}) =  \delta(x_N-x_0)\prod_{j=0}^{N}e^{-\frac{(x_{j+1}-x_j)^2}{2\Delta T}},
\end{equation}
and completing the square in the exponents to decouple the Gaussians.  
Note their version uses $\sum_{j}x_j=0$ to fix $y_N$.  
The Jacobian can be shown to unity, since the matrix is upper diagonal, with unit diagonal.  
\item \textbf{Tests}
\item Compare to parallel plate energy to get convergence. 
\item Give some consideration to finite $\lambda$ in potential.  
\begin{equation}
V(x) = \lambda\int_{\Sigma}d\sigma \delta(x-x\sigma)
\end{equation}
where $\Sigma$ is a $d-1$ dimensional surface, $\sigma$ is a reparameterization invariant measure and $x_\sigma$ points to the surface.  
\item For interaction energies, need $(e^{-V_{1+2}} - 1) -  (e^{-V_1}-1) - (e^{-V_{2}}-1)$.  If only touch one surface (of disconnected bodies) then 
no contribution, since $V_{1+2}=V_1$
\item Then consider massless scalar between sphere/plate and cylinder plate.  
\item Consider breakdown of PFA as function of separation $a$ to sphere radius $R$.  
\item \textbf{Conclusions}
\item Needs no underlying symmetry.  Precision hinges on loop parameters chosen (and presumably discretization of surfaces)
\item Claim their delta potentials are ``hard''.
\item Note finite temperature and roughness required.  
\item Note numerical differentiation to get force is hard, but derivative can be done right off the bat.  (And energy-momentum tensors)
\item Cite Feinberg and Sucher for possible path for EM quantization.  
\end{itemize}

\subsubsection{Gies2001}
\cite{Gies2001}

Use worldlines to compute EM effective action in specified background EM field, modelling interaction with scalar particle.  

\subsubsection{Gies 2006}
\cite{Gies2006}

Very similar?  Advances?  
D-loops?  Note similarity to methods of generating brownian walks by doubling intermediate points to improve resolution where required.  

\subsubsection{Gies 2006 a}
\cite{Gies2006a}

\subsection{Papers: Thermal worldlines}

\subsubsection{Geothermal2008:Klingm\"uller}
~\cite{Klingmueller2008}.  
\subsubsection{Weber2009:Inclined planes}
~\cite{Weber2009}
\subsubsection{Weber2009:Interplay}
~\cite{Weber2010}
\subsubsection{Weber2009:Spheres}
\cite{Weber2010a}.  

\subsubsection{Schaden:Pistons}

Cite Schaden applying to pistons\cite{Schaden2009}

Why?  What for?  Benefits?

\subsection{Nearby attempts}

\cite{Aehlig2011}

\cite{Maggs2006, Pasquali2008}

\section{Papers:Stochastic Methods}

\subsection{Gradients}

\subsection{Feynman-Kac}

\subsubsection{Hooghiemstra}



\section{Papers:Dielectric Quantization}



\subsection{Vogel and Welsch}


%\cite{Dung1998}
\cite{Raabe2006}
\cite{Raabe2007}

\subsection{Huttner/Barnett}

\cite{Glauber1991}

\cite{Huttner1992}

\cite{Matloob1995}
\cite{Matloob1996}


\subsection{Philbin}

\cite{Philbin2010}
\cite{Philbin2011}

\cite{Drummond2014}

\subsection{Bordag}
\cite{Bordag1998} \cite{Bordag1999}

\subsection{Bechler}

\cite{Bechler1999}
\cite{Bechler2006}

\section{Quantization in dielectric}


\subsection{Rosa2010}

Justifies/derives why it is okay to use neglect dispersion in derivations
of the Casimir energy.  i.e. okay to set things up with real $\epsilon$,
then take $\epsilon\rightarrow\epsilon(i\omega_n)$.  \cite{Rosa2010}

The classical energy density in a dispersive medium is (Eq. 1)
\begin{equation}
  \bar{u}(\vect{r},\omega) = 
  \left[\frac{d(\omega\epsilon_R)}{d\omega}|\vect{E}_\omega(\vect{r})|^2 +
    \frac{d(\omega\mu_R)}{d\omega}|\vect{H}_\omega(\vect{r})|^2\right],
\end{equation}
where $\epsilon_R,\mu_R$ are the real parts of the permittivity and magnetic 
permeability.  This is neglecting dispersion. 
Apparently this also holds in the quantum theory, at finite temperature,
with or without dispersion \emph{in uniform media}.  
(They note relation to Barash and Ginzburg)

Use harmonic model and carefully add up contributions from each dipole.
Define energy based on integral of Poynting's theorem.  


\section{Quantum Trajectories}

\subsection{Carmichael}
Cite Carmichael Rice JOSA paper.\cite{Carmichael1989,Carmichael1991}

Cite Carmichael 1993 lectures. \cite{Carmichael1993}

\subsection{Others}

Cite Marte
Cite Parkins  
Cite Gardiner \cite{Gardiner1992}
Cite Marte, Zoller, Parkins, Gardiner (MCWF) \cite{Dalibard1992}
\cite{Dum1992}

\subsection{Path integral version}


\subsection{Measuring atom positions}

Measurement of atom's\cite{Caves1987}


 Cite Holland, Meystre.  Applied to position measurements of atoms by detecting photons.  Detection of photons localizes atoms.  
\cite{Holland1996}

Motion in optical lattice
\cite{Greenwood1997}

Lose spatial coherence from single emission.
\cite{Pfau1994}

Which-way \cite{Gagen1993}


\subsection{Holland1996}

Consider imaging the resonance fluorescence of 2-level atom on a detector.  We want 
to build up the quantum trajectory picture.  
This is closer to what would actually be done in an experiment, rather than the typical
choice of angle-resolved detection.  

The decay operators for a 2-level atom emitting light into free space  plane wave modes are
\begin{equation}
  \hat{a}_{\mu\Lambda} = \sum_\sigma\vect{\epsilon}_\sigma\cdot\vect{\epsilon}^*_{\mu\Lambda}
  \hat{A}_\sigma e^{-ik\vect{u}\cdot\vect{r}}
\end{equation}
where $\sigma$ are polarization labels, $\epsilon_i$ are polarization vectors, $\hat{A}_\sigma$
is the internal lowering operator (with a $\sqrt{\gamma}$), $k$ is the wavelength of light emitted
in direction of the unit vector $\vect{u}$, at position $\vect{r}$.  

Using these operators corresponds to angle-resolved photon detection.  
If we pass the photons through a infinite thin lens, we can get a position based detection.
(Set up the atomic dipole to emit in a particular direction)
This relies of the fact that in the paraxial approximation, 
the combination of propagation, with a thin lens acts as a Fourier transform.
\subsubsection{Fourier Optics}

Conventions borrowed from Stek Classical Optics.  (Also see Fox Fourier Analysis)

\begin{itemize}
  \item Take 2-d Fourier transform of electric field.  
  \item Propagate with $e^{i\sqrt{k^2-k_x^2-k_y^2}z}$.  
  \item Invert Fourier transform at end to get final electric field distribution.  
  \item In paraxial approximation, use $e^{ik z- i(k_x^2+k_y^2)z/(2k)}$.
  \item Thin spherical lens is a quadratic phase mask.  $e^{-i(x^2+y^2)/(2f)}$.
  \item For propagating and inverting we get: 
    \begin{align}
      E(x',y',z) 
      &=  \int \frac{dk_xdk_y}{(2\pi)^2} e^{ik_xx' +ik_yy'}e^{ikz - i(k_x^2+k_y^2)z/(2k)}\int dx dy e^{-ik_xx-ik_y y} E_0(x,y)\\
      &= e^{ikz}\int dx dy \int \frac{dk_xdk_y}{(2\pi)^2} e^{-ik_x(x-x')-ik_y(y-y')}e^{-i(k_x^2+k_y^2)z/(2k)}E_0(x,y)\\
      &= e^{ikz}\int dx dy \bigg( \frac{k}{2\pi i z}\bigg)e^{i[k_x(x-x')^2+k_y(y-y')^2]z/(2k)}E_0(x,y)
    \end{align}
    Combination of propagate-lens-propagate is 
    \begin{equation}
      \tilde{E}_0(k_x,k_y) =  e^{ikz - i(k_x^2+k_y^2)z/(2k)}\int dx dy e^{-ik_xx-ik_y y} E_0(x,y)
    \end{equation}
    \begin{align}
      E(x_2,y_2,z) &= e^{ik(z_1+z_2)}\int dx_1dy_1 \int dx dy \bigg( \frac{ik}{2\pi z_1}\bigg)\bigg( \frac{ik}{2\pi z_2}\bigg)
      \nonumber \\ 
      & \times e^{ik[(x_2-x_1)^2+(y_2-y_1)^2]/(2z_2)}e^{-ik(x_1^2+y_1^2)/(2f)} e^{ik[(x-x_1)^2+(y-y_1)^2]/(2z_1)}E_0(x,y)
    \end{align}
    If we set $z_1=z_2=f?$  This eliminates one set of  quadratic terms in $x_1,y_1$.  Leaving something like 
    \begin{align}
      E(x_2,y_2,z) &= e^{ik(z_1+z_2)}\int dx_1dy_1 \int dx dy \bigg( \frac{ik}{2\pi z_1}\bigg)^2
      e^{ik[x_2^2-2x_1(x_2+x) +x_1^2 +x^2 + y_2^2-2y_1y_2 +y_1^2 +y^2]/(2z)}E_0(x,y)\\
      &= e^{2ikf+ik(x_2^2+y_2^2)/2f}\int dx_1dy_1 \int dx dy \bigg( \frac{ik}{2\pi f}\bigg)^2
      e^{ik[(x_1-x_2-x)^2-(x_2+x)^2 +x^2 +(y_1-y_2-y)^2-(y_2-y)^2 +y_1^2 +y^2]/(2f)}E_0(x,y)\\
      &= e^{2ikf}\frac{ik}{2\pi f} \int dx dy e^{ik(xx_2+yy_2)/f}E_0(x,y)
    \end{align}
    Huzzah for re-proving the obvious.  
\end{itemize}

Use two lenses (to account for emission into the forwards/backwards hemispheres).  
The operators are then 
\begin{align}
  \op{a}_{\nu\Lambda \zeta} = \int dx dy e^{ik \vect{u}\cdot\op{\vect{x}}-ik}
\end{align}

In one dimension this becomes 
\begin{align}
  \op{a}_{u\sigma} = \sqrt{N_{u\sigma}}\op{A}_\sigma e^{-ik u \op{x}}.
\end{align}
where $N_{u\sigma}$ is the relevant dipole emission pattern for $\sigma=0,\pm 1$, $u=k_x$.



\subsection{Control theory}
 Control Theory.  Cite Wiseman book.   \cite{WisemanMilburn2010}

Doherty and Jacobs \cite{Doherty1999}

Cite Steck feedback control paper.  \cite{Steck2004, Steck2006}

\subsection{Quantum chaos}

Cite Bhattacharya quantum paper.  \cite{Bhattacharya2000}

\subsection{Noisy measurements}
Cite Warshawski/Wiseman \cite{Warszawski2003a,Warszawski2003b}

Cite Jeremy Thorne.  


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis_master"
%%% End: 
