\abstract{
The Casimir effect refers to the primarily attractive force between material bodies due to quantum fluctuations
in the electromagnetic field.  The Casimir effect is difficult to calculate in general, since it 
is sensitive to the exact shapes of the bodies and involves contributions from all frequencies.
As a result, calculating the Casimir effect between general bodies usually requires a numerical approach.
The worldline method computes Casimir energies by creating an ensemble of space-time paths corresponding
to a virtual particle interacting with the bodies.
This method was originally developed for a scalar fields coupled to an idealized background
potential, rather than the vector electromagnetic field interacting with media.

This thesis presents work on extending the worldline method to account for the material properties 
of the interacting bodies, and the polarizations of electromagnetism.
% The electromagnetic worldline method will be developed  for the case of planar geometries 
% of bodies, with the goal of developing a method that holds in arbitrary arrangements of bodies.  
This thesis starts by covering background material on path integrals, 
and quantizing the electromagnetic field in media.
The electromagnetic field is decomposed in terms of two scalar fields for planar bodies,
 where these scalar fields correspond to the transverse-electric and transverse-magnetic polarizations of the electromagnetic field.
The worldline path integrals are developed for both polarizations, and solved analytically.
Next, numerical methods are developed and tested in the context of planar bodies.  
The starting positions, and scale of the paths, and shape of the paths are sampled via Monte Carlo methods.
The transverse-magnetic path integral also requires specialized methods for estimating derivatives, and path construction.
The analytical and numerical results for both worldline path integrals are in agreement with known solutions.
Finally, specialized methods are developed for computing derivatives of the worldline Casimir-energy path integrals,
allowing for efficient numerical computations of Casimir forces and torques.
}


